---
title: "AAQ"
author: "Austin Fisenko"
date: "3/17/2021"
output: html_document
---

# Setup
Empty environment, loading library, set knitr and scientific notation
```{r setup}
# Empty Global Environment
rm(list = ls())

source("Upload Preparation.R")
NDA_AAQ <- read.csv("acceptance01_template.csv", skip = 1)
options(digits = 3)
```

# Prep Sheet
Create prep sheet to begin transferring data into NDA format.
```{r Prep Sheet}
UO_AAQ <- select(UO_Qualtrics, c(Fam_ID, subjectkey, src_subject_id, interview_date, interview_age_Mom, sex_mother, GroupAssignment, Timepoint = Timepoint.x,contains("srm_aaq")))
UPMC_AAQ <- select(UPMC_Qualtrics, c(Fam_ID, subjectkey, src_subject_id, interview_date, interview_age_Mom, sex_mother, GroupAssignment, Timepoint = Timepoint.x,contains("srm_aaq")))

# Bind tw site from two site 
AAQ_Prep <- bind_rows(UO_AAQ,UPMC_AAQ)

# Clean global Environment
rm(UO_AAQ, UPMC_AAQ, UO_Qualtrics, UPMC_Qualtrics, Pedigree, Redcap_Data, UO_Qualtrics_T1, UO_Qualtrics_T2, UO_Qualtrics_T3, UO_Qualtrics_T4, UO_Qualtrics, UO_Qualtrics_list, UPMC_Qualtrics_T1, UPMC_Qualtrics_T2, UPMC_Qualtrics_T3, UPMC_Qualtrics_T4, UPMC_Qualtrics, UPMC_Qualtrics_list)
```

# Re-code
Convert Likert Scale text input into numerical values then create a dataframe to place ID's that do not have 67% of their data present.
```{r Re-code and 67% Rule}
# Recode text responses into numbers so they can be used in calculations
new_AAQ_names <- paste("srm_aaq", seq(1:10), sep = '_')

AAQ_Prep <- AAQ_Prep %>% 
  mutate_at(new_AAQ_names,
            funs(recode(., "1 Never True" = 1, 
                        "2 Very Rarely True" = 2,
                        "3 Seldom True" = 3,
                        "4 Sometimes True" = 4,
                        "5 Often True" = 5,
                        "6 Almost Always True" = 6,
                        "7 Always True" = 7,.default = NaN)))

# Recode UPMC Group Assignment names to match UO Group Assignment names
AAQ_Prep <- AAQ_Prep %>% 
  mutate_at(c("GroupAssignment"),
            funs(recode(., "Assigned Group 3 (HC)" = "Healthy", 
                        'Assigned Group 2 (FSU)' = "NO DBT",
                        'Assigned Group 1 (DBT)' = "DBT")))

# Check NA percentage
AAQ_Prep$NACheck <- rowSums(is.na(select(AAQ_Prep, starts_with("srm"))))/ncol(dplyr::select(AAQ_Prep, starts_with("srm")))

# Drop people who are less than 67% & 100%
AAQ_Drop_67 <- AAQ_Prep[AAQ_Prep$NACheck > 0.67, ]
AAQ_Prep_67 <- AAQ_Prep[AAQ_Prep$NACheck <= 0.67, ]

AAQ_Drop_100 <- AAQ_Prep[AAQ_Prep$NACheck > 0, ]
AAQ_Prep_100 <- AAQ_Prep[AAQ_Prep$NACheck <= 0, ]

```

# Calculated Columns
Create sums column for AAQ total. 
```{r calculated columns}
# Create calculated columns for 67% version of the Prep Sheet
#AAQ_Prep_67 <- add_column(AAQ_Prep_67, aaq_total = rowSums(AAQ_Prep_67[, c("srm_aaq_1", "srm_aaq_2", #"srm_aaq_3", "srm_aaq_4", "srm_aaq_5", "srm_aaq_6", "srm_aaq_7", 
#                                                                   "srm_aaq_8", "srm_aaq_9", #"srm_aaq_10")]),.after = "srm_aaq_10")

AAQ_Prep <- add_column(AAQ_Prep, aaq_total = rowSums(AAQ_Prep[, c("srm_aaq_1", "srm_aaq_2", "srm_aaq_3", "srm_aaq_4", "srm_aaq_5", "srm_aaq_6", "srm_aaq_7", 
                                                                   "srm_aaq_8", "srm_aaq_9", "srm_aaq_10")]),.after = "srm_aaq_10")

AAQ_Prep_100 <- add_column(AAQ_Prep_100, aaq_total = rowSums(AAQ_Prep_100[,c("srm_aaq_1", "srm_aaq_2", "srm_aaq_3", "srm_aaq_4", "srm_aaq_5", "srm_aaq_6", "srm_aaq_7", "srm_aaq_8", "srm_aaq_9", "srm_aaq_10")]),.after = "srm_aaq_10")

```

# NDA Sheet
Re-name AAQ Prep Sheet columns to match NDA specifications. 
```{r NDA Sheet}
# Create NDA prep sheet
# Select all the needed columns from CBCL_Prep sheet
NDA_AAQ_Prep <- select(AAQ_Prep, c(subjectkey, src_subject_id, interview_date, interview_age = interview_age_Mom, sex = sex_mother, visit = Timepoint,  aaq_score = aaq_total, starts_with("srm")))

# Create NDA structure column names, they are unique and without a pattern so they must be made manually 
NDA_AAQ_Names <- paste(c("aaq2_1", "aaq_1_16", "aaq2_3", "aaq2_4", "aaq2_5", "aaq32", "aaq2_6", "aaq24", "aaq2_8", "aaq2_9"))

# Change names in the NDA_CBCL_Prep to match the NDA structure column names
setnames(NDA_AAQ_Prep, new_AAQ_names, NDA_AAQ_Names)

# Make an empty row in the NDA sheet for compatibility (to avoid some potential errors)
NDA_AAQ[1,] <- NA

# Combine NDA CBCL Prep sheet with the NDA structure
NDA_AAQ <- bind_rows(NDA_AAQ,NDA_AAQ_Prep)

# Recreate first line in orignial NDA file
# Make an empty row, with same number of column in NDA_CBCL, as first line of NDA sheet
# ncol(NDA_CBCL)  is number of columns in NDA_CBCL
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_AAQ))

# assign the first cell in first_line as acceptance which is the first cell in orignial NDA structure
first_line[,1] <- "acceptance"

# assign the second cell in first_line as "1"
first_line[,2] <- "1"

# Create a new file in folder called cbcl1_5.csv, and put first line into this file
# acceptance01.csv file will be saved into same folder as this current r script
write.table(first_line, file = "acceptance01.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = FALSE, row.names = FALSE)

# Append data in NDA_AAQ into acceptance01.csv file 
write.table(NDA_AAQ, file = 'acceptance01.csv', sep = ",", append = TRUE, na = "", quote = FALSE, row.names = FALSE)

# Clean environment of intermediate calculations for NDA structure
rm(NDA_AAQ_Prep, NDA_AAQ_Names, first_line, New_AAQ_Names)

```

# Table
Create descriptives means table.
```{r Table}
#install.packages("knitr")
#install.packages("magrittr")
#install.packages("kableExtra")

library(knitr)
library(magrittr)
library(kableExtra)

# Select necessary columns for means table
Progress <- select((AAQ_Prep), c(Fam_ID, GroupAssignment, Timepoint, starts_with("srm"), aaq_total))

# Calculate row mean for each individual
Progress$Row_Mean <- rowMeans(select(AAQ_Prep, c(starts_with("srm"))), na.rm = T)

# Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$Fam_ID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

# Group by GroupAssignment and Timepoint, and calcultae Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint, site) %>%
  summarise(GroupMean = mean(aaq_total, na.rm = T), count = n())

# Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Calculate mean from both sites
Both_Site_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSiteMean_AAQ = mean(aaq_total, na.rm = T), n = sum(count = n()))

# Change GroupMean column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_AAQ"
colnames(UO)[colnames(UO) == "count"] = "UO_AAQ_Original_N"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_AAQ"
colnames(UPMC)[colnames(UPMC) == "count"] = "UPMC_AAQ_Original_N"
colnames(Both_Site_Mean)[colnames(Both_Site_Mean) == "n"] = "BothSite_Original_N"

# Combine UO, UPMC, and Both_Site data 
Mean_Table <- data.frame(UO[,c("UO_AAQ","GroupAssignment")],UPMC[,"UPMC_AAQ"],Both_Site_Mean[,c("BothSiteMean_AAQ","BothSite_Original_N")])

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

# Re-order Mean Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Create Table
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("AAQ Table Means (67%)" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = F) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

# 100% Table
Create descriptives table for only ID's that have 100% of their data.
```{r 100% Table}
# Select necessary columns for means table
Progress <- select((AAQ_Prep_100), c(Fam_ID, GroupAssignment, Timepoint, starts_with("srm"), aaq_total))

# Calculate row mean for each individual
Progress$Row_Mean <- rowMeans(select(AAQ_Prep_100, c(starts_with("srm"))), na.rm = T)

# Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$Fam_ID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

# Group by GroupAssignment and Timepoint, and calculate Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint, site) %>%
  summarise(GroupMean = mean(aaq_total, na.rm = T), count = n())

# Select only UO Mean
UO100 <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean
UPMC100 <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Calculate mean from both sites
Both_Site_Mean100 <- Progress %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSiteMean_AAQ = mean(aaq_total, na.rm = T), n = sum(count = n()))

# Change GroupMean column names according to site
colnames(UO100)[colnames(UO100) == "GroupMean"] = "UO_AAQ"
colnames(UO100)[colnames(UO100) == "count"] = "UO_AAQ_100_N"
colnames(UPMC100)[colnames(UPMC100) == "GroupMean"] = "UPMC_AAQ"
colnames(UPMC100)[colnames(UPMC100) == "count"] = "UPMC_AAQ_100_N"
colnames(Both_Site_Mean100)[colnames(Both_Site_Mean100) == "n"] = "BothSite_AAQ_100_N"

# Combine UO, UPMC, and Both_Site data 
Mean_Table <- data.frame(UO100[,c("UO_AAQ","GroupAssignment")],UPMC100[,"UPMC_AAQ"],Both_Site_Mean100[,c("BothSiteMean_AAQ","BothSite_AAQ_100_N")])

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

# Re-order Mean Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Add a header
install.packages(knitr)

# Create Table
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("AAQ Table Means (100%)" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = F) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

# N Table
Create table for participant numbers.
```{r N Table}
# Create N table, GroupAssignment and Timepoint are dupliced here, just checking it's align

N <- data.frame(UO[, c("Timepoint", "UO_AAQ_Original_N", "GroupAssignment")],
                UO100[, c("Timepoint", "UO_AAQ_100_N", "GroupAssignment")],
                UPMC[, c("Timepoint", "UPMC_AAQ_Original_N", "GroupAssignment")],
                UPMC100[, c("Timepoint", "UPMC_AAQ_100_N", "GroupAssignment")],
                Both_Site_Mean[,c("Timepoint", "BothSite_Original_N", "GroupAssignment")],
                Both_Site_Mean100[,c("Timepoint", "BothSite_AAQ_100_N", "GroupAssignment")]
                )
# Remove dupliced column 
N <- N[,-c(1,3,4,6,7,9,10,12,13,15,16,18,19,21,22,24,25,27)]


# Convert data frame to numeric
N <- as.data.frame(sapply(N, as.numeric))

# Transfer N table from Horzontal to Vertical
N <- data.frame(t(N))

# Calculate Total N 
N$T1 <- rowSums(N[,c(1,5,9)])
N$T2 <- rowSums(N[,c(2,6,10)])
N$T3 <- rowSums(N[,c(3,7,11)])
N$T4 <- rowSums(N[,c(4,8,12)])

# Timepoint names 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4", "T1","T2", "T3", "T4")

# Rename column name 
setnames(N, names(N), Timepoint_names)

# Create Table
kable(N) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  add_header_above(c(" " = 1, "DBT Group" = 4, "Control Group" = 4, "FSU Group" = 4, "Totals" = 4)) %>%
  add_header_above(c("Participant Numbers" = 17)) %>%
  column_spec(c(1,5,9,13), border_right = T, include_thead = F) %>%
  column_spec(1:16, width_min = "2cm", width_max = "5cm") %>%
  row_spec(1:6, background = "#d3d3d3")
```