---
title: "PKBS"
author: START Lab
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
# Empty Global Enivronment
rm(list = ls())
```

## Import
Import Qualtrics excel files into R
```{r Import}
#Install Package, this only need to be done once.
install.packages(c("dplyr","tidyverse","data.table","contrib.url","knitr"))
install.packages('plyr', repos = "http://cran.us.r-project.org")

#Load packages, this need to be done every time you run this script. 
library(dplyr)
library(tidyverse)
library(data.table)
library(knitr)

#Set Working Directory
setwd("~/Documents/GitHub/DataUploadAutomation/Measures/PKBS/DataUploadAutomation/Measures/PKBS/")

#Import Pedigree and NDA Structure
Pedigree <- read.csv("Reference_Pedigree.csv")
NDA_PKBS <- read.csv("pkbs01_template.csv", skip = 1)

#Import PKBS files from both sites and every timepoint
UO_T1_PKBS <- read.csv("UO_T1_Qualtrics.csv", stringsAsFactors = FALSE)
UPMC_T1_PKBS <- read.csv("UPMC_T1_PKBS.csv", stringsAsFactors = FALSE)
UO_T2_PKBS <- read.csv("UO_T2_Qualtrics.csv", stringsAsFactors = FALSE)
UPMC_T2_PKBS <- read.csv("UPMC_T2_PKBS.csv", stringsAsFactors = FALSE)
UO_T3_PKBS <- read.csv("UO_T3_Qualtrics.csv", stringsAsFactors = FALSE)
UPMC_T3_PKBS <- read.csv("UPMC_T3_PKBS.csv", stringsAsFactors = FALSE)
UO_T4_PKBS <- read.csv("UO_T4_Qualtrics.csv", stringsAsFactors = FALSE)
UPMC_T4_PKBS <- read.csv("UPMC_T4_PKBS.csv", stringsAsFactors = FALSE)
```

## Rename Columns
Rename questions numbers to self-report measure scale items. Then, take each scale measure from both sites and combine them by timepoint.
```{r Rename Columns}
#Rename variables that we want to select for PKBS
#Create list of new variable names
pkbs <- "srm_pkbs"
num_items <- seq(1:33)
new_PKBS_names <- paste(pkbs, num_items, sep='_')

#Now make a list of old variables names so that we can replace them with the neww ones
UO_Q407 <- "Q407"
UO_Q359 <- "Q359"
UO_Q524 <- "Q524"
UO_Q817 <- "Q817"
UPMC_Q16 <- "Q16.1"
UPMC_Q13 <- "Q13.1"
old_UO_PKBS_names <- paste(UO_Q407, num_items,sep = "_")
old_UO_PKBS_names2 <- paste(UO_Q359, num_items,sep = "_")
old_UO_PKBS_names3 <- paste(UO_Q524, num_items,sep = "_")
old_UO_PKBS_names4 <- paste(UO_Q817, num_items,sep = "_")
old_UPMC_PKBS_names <- paste(UPMC_Q16, num_items,sep = "_")
old_UPMC_PKBS_names2 <- paste(UPMC_Q13, num_items, sep = "_")

#Change UO column names
setnames(UO_T1_PKBS, old_UO_PKBS_names, new_PKBS_names, skip_absent=FALSE)
setnames(UO_T2_PKBS, old_UO_PKBS_names2, new_PKBS_names, skip_absent=FALSE)
setnames(UO_T3_PKBS, old_UO_PKBS_names3, new_PKBS_names, skip_absent=FALSE)
setnames(UO_T4_PKBS, old_UO_PKBS_names4, new_PKBS_names, skip_absent=FALSE)

#Change UPMC column names
setnames(UPMC_T1_PKBS, old_UPMC_PKBS_names, new_PKBS_names, skip_absent=FALSE)
setnames(UPMC_T2_PKBS, old_UPMC_PKBS_names2, new_PKBS_names, skip_absent=FALSE)
setnames(UPMC_T3_PKBS, old_UPMC_PKBS_names2, new_PKBS_names, skip_absent=FALSE)
setnames(UPMC_T4_PKBS, old_UPMC_PKBS_names, new_PKBS_names, skip_absent=FALSE)

#Edit UO PKBS Times 1-4 to have only PKBS questions and the FamID
UO_T1_PKBS <- select(UO_T1_PKBS, c(FamID = Q221, contains("pkbs")))
UO_T2_PKBS <- select(UO_T2_PKBS, c(FamID = Q116, contains("pkbs")))
UO_T3_PKBS <- select(UO_T3_PKBS, c(FamID = Q174, contains("pkbs")))
UO_T4_PKBS <- select(UO_T4_PKBS, c(FamID = Q203, contains("pkbs")))

#Edit UPMC PKBS Times 1-4 to have only PKBS questions and the FamID
UPMC_T1_PKBS <- select(UPMC_T1_PKBS, c(FamID = Q1.2, contains("pkbs")))
UPMC_T2_PKBS <- select(UPMC_T2_PKBS, c(FamID = Q1.2, contains("pkbs")))
UPMC_T3_PKBS <- select(UPMC_T3_PKBS, c(FamID = Q1.2, contains("pkbs")))
UPMC_T4_PKBS <- select(UPMC_T4_PKBS, c(FamID = Q1.2, contains("pkbs")))

#Merge UO and UPMC data by Timepoint
PKBS_T1 <- rbind(UO_T1_PKBS, UPMC_T1_PKBS)
PKBS_T2 <- rbind(UO_T2_PKBS, UPMC_T2_PKBS)
PKBS_T3 <- rbind(UO_T3_PKBS, UPMC_T3_PKBS)
PKBS_T4 <- rbind(UO_T4_PKBS, UPMC_T4_PKBS)

#Clean up environment
# rm(UO_T1_PKBS, UO_T2_PKBS, UO_T3_PKBS, UO_T4_PKBS, UPMC_T1_PKBS, UPMC_T2_PKBS, UPMC_T3_PKBS, UPMC_T4_PKBS)
```

## Prep Sheet
Create prep sheet to begin transferring data into NDA format. Rename relevant GUID information to match NDA specifications. Finally, bind all timepoints into single PKBS Prep Sheet.
```{r Prep Sheet}
#Create the Pedigree table for each timepoint
Pedigree_T1 <- select(Pedigree, FamID, FamID_Mother, mom_guid, MomGender, Time1Date, MomAge_T1, GroupAssignment)
Pedigree_T2 <- select(Pedigree, FamID, FamID_Mother, mom_guid, MomGender, Time2Date, MomAge_T2, GroupAssignment)
Pedigree_T3 <- select(Pedigree, FamID, FamID_Mother, mom_guid, MomGender, Time3Date, MomAge_T3, GroupAssignment)
Pedigree_T4 <- select(Pedigree, FamID, FamID_Mother, mom_guid, MomGender, Time4Date, MomAge_T4, GroupAssignment)

#Merge Pedigree data to PKBS timepoints
PKBS_T1 <- merge(Pedigree_T1, PKBS_T1, by = "FamID")
PKBS_T2 <- merge(Pedigree_T2, PKBS_T2, by = "FamID")
PKBS_T3 <- merge(Pedigree_T3, PKBS_T3, by = "FamID")
PKBS_T4 <- merge(Pedigree_T4, PKBS_T4, by = "FamID")

#Clean up environment
rm(Pedigree, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)

#Create new column designating time point for each database
PKBS_T1$Timepoint <- "Time 1"
PKBS_T2$Timepoint <- "Time 2"
PKBS_T3$Timepoint <- "Time 3"
PKBS_T4$Timepoint <- "Time 4"

#Rename each of the Date and Age columns so that they match
PKBS_T1 <- PKBS_T1 %>% rename( interview_date = Time1Date, interview_age = MomAge_T1)
PKBS_T2 <- PKBS_T2 %>% rename( interview_date = Time2Date, interview_age = MomAge_T2)
PKBS_T3 <- PKBS_T3 %>% rename( interview_date = Time3Date, interview_age = MomAge_T3)
PKBS_T4 <- PKBS_T4 %>% rename( interview_date = Time4Date, interview_age = MomAge_T4)

#Merge all timepoints together to create the PKBS prep sheet
PKBS_Prep <- rbind(PKBS_T1, PKBS_T2, PKBS_T3, PKBS_T4)

#Change gender to F instead of FALSE
PKBS_Prep$MomGender <- "F"


#Clean up environment
# rm(PKBS_T1, PKBS_T2, PKBS_T3, PKBS_T4)
```

## Re-code and Reverse Score
```{r Re-code and Reverse Score}
#Turn Likert Scale from text string to numeric value
PKBS_Prep[PKBS_Prep == "Never (0)"] <- 0; PKBS_Prep[PKBS_Prep == "Rarely (1)"] <- 1;
PKBS_Prep[PKBS_Prep == "Sometimes (2)"] <- 2; PKBS_Prep[PKBS_Prep == "Often (3)"] <- 3;
```

## Calculated Columns
Create sums column combining each individual measure. 
```{r Calculated Columns}
# Change number to numeric values and Create Calculated Column 
PKBS_Prep[,8:40] <- sapply(PKBS_Prep[,8:40],as.numeric)

PKBS_Prep  <- add_column(PKBS_Prep, pkbs_total = rowSums(PKBS_Prep[, c("srm_pkbs_1", "srm_pkbs_2","srm_pkbs_3","srm_pkbs_4", "srm_pkbs_5", "srm_pkbs_6",
                                                                       "srm_pkbs_7", "srm_pkbs_8", "srm_pkbs_9", "srm_pkbs_10", "srm_pkbs_11", "srm_pkbs_12", "srm_pkbs_13",
                                                                       "srm_pkbs_14", "srm_pkbs_15", "srm_pkbs_16", "srm_pkbs_17", "srm_pkbs_18", "srm_pkbs_19", "srm_pkbs_20",
                                                                       "srm_pkbs_21", "srm_pkbs_22", "srm_pkbs_23", "srm_pkbs_24", "srm_pkbs_25", "srm_pkbs_26", "srm_pkbs_27",
                                                                       "srm_pkbs_28", "srm_pkbs_29", "srm_pkbs_30", "srm_pkbs_31", "srm_pkbs_32", "srm_pkbs_33")]),.after = "srm_pkbs_33")

```

## NDA Sheet
Re-name PKBS Prep Sheet columns to match NDA specifications. 
```{r NDA Sheet}
#Create list of column names for PKBS prep and NDA structure
NDA_PKBS_Prep <- select(PKBS_Prep, c(visit = "Timepoint", subjectkey = "mom_guid", src_subject_id = "FamID_Mother", sex = "MomGender", interview_age, GroupAssignment, interview_date, starts_with("srm"), pkbs_total))


NDA_names <- c("Social2", "Social7", "Social10", "Social12", "Social16", "Social22", "Social23", "Social25", 
               "Social28", "Social29", "Social30", "Social32", "Social5", "Social14", "Social15", "Social17", 
               "Social19", "Social20", "Social21", "Social24", "Social27", "Social33", "Social34", "Social1", 
               "Social3", "Social6", "Social8", "P_soc_23_ft", "Social11", "Social13", "Social18", "Social26", 
               "Social31")

setnames(NDA_PKBS_Prep, new_PKBS_names, NDA_names, skip_absent = FALSE)
colnames(NDA_PKBS_Prep)[40] <- "basc_social_raw"


#Merge PKBS Prep Sheet into NDA structure
NDA_PKBS[1,] <- NA
NDA_PKBS <- bind_rows(NDA_PKBS_Prep, NDA_PKBS)

#Recreate the first line of the NDA
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_PKBS))
first_line[,1] <- "pkbs"
first_line[,2] <- "1"
```

## Table
Create descriptive means table.
```{r}
library(knitr)
library(magrittr)
library(kableExtra)

#Select necessary columns for means table
Progress <- select((PKBS_Prep), c(FamID, GroupAssignment, Timepoint, starts_with("srm"), pkbs_total))

#Calculate row mean for each individual
Progress$Row_Mean <- rowMeans(select(PKBS_Prep, c(starts_with("srm"))), na.rm = T)

#Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$FamID))

#Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

#Group by GroupAssignment and Timepoint, and calcultae Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint, site) %>%
  summarise(GroupMean = mean(pkbs_total, na.rm = T), count = n())

#Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
#Select only UPMC Mean
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

#Calculate mean from both sites
Both_site_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSiteMean = mean(pkbs_total, na.rm = T), n = sum(count = n()))

#Change GroupMean column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_PKBS"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_PKBS"

#Combine UO, UPMC, and Both_Site data 
Mean_Table <- data.frame(UO[,c("UO_PKBS","GroupAssignment")],UPMC[,"UPMC_PKBS"],Both_site_Mean[,c("BothSiteMean","n")])

#Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

#Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

#Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

#Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

#Add a header
install.packages(knitr)

kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("PKBS Table Means" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")



```

