---
title: "CBCL"
author: "Austin Fisenko"
date: "7/9/2020"
output: html_document
---

```{r setup}
# Loading Library
library(dplyr)
library(data.table)
library(knitr)
library(kableExtra)
library(tidyverse)

# Settings for knit the whole document 
# Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
knitr::opts_chunk$set(echo = TRUE, include = FALSE)

# scientific notation, round up to 3 digits
options(digits = 3)

```

# Import
Import Qualtrics excel files into R
```{r Import}
# Empty Global Environment
rm(list = ls())

# Import Pedigree and NDA Structure
Pedigree <- read.csv("Reference_Pedigree.csv")
NDA_CBCL <- read.csv("cbcl1_501_template.csv", skip = 1)

# Import UO and UMPC flies, data is kept from being factors so later modifications will work
UO_T1_CBCL <- read.csv(file = 'UO_T1_Qualtrics.csv', stringsAsFactors = FALSE)
UO_T2_CBCL <- read.csv(file = 'UO_T2_Qualtrics.csv', stringsAsFactors = FALSE)
UO_T3_CBCL <- read.csv(file = 'UO_T3_Qualtrics.csv', stringsAsFactors = FALSE)
UO_T4_CBCL <- read.csv(file = 'UO_T4_Qualtrics.csv', stringsAsFactors = FALSE)

UPMC_T1_CBCL <- read.csv(file = 'UPMC_T1_cbcl.csv', stringsAsFactors = FALSE)
UPMC_T2_CBCL <- read.csv(file = 'UPMC_T2_cbcl.csv', stringsAsFactors = FALSE)
UPMC_T3_CBCL <- read.csv(file = 'UPMC_T3_cbcl.csv', stringsAsFactors = FALSE)
UPMC_T4_CBCL <- read.csv(file = 'UPMC_T4_cbcl.csv', stringsAsFactors = FALSE)

```

# Rename Columns
Rename questions numbers to self-report measure scale items. Then, take each scale measure from both sites and combine them by timepoint.
```{r Rename Columns}
# Create list of new variable names for the Prep Sheet
New_CBCL_Names <- sprintf("srm_cbcl_%03d", seq(1:100))

# Create list of old variable names so we can target them to be replaced with the new ones
# Since the question names change by timepoint we'll have to make unique lists by timepoint, starting with UO Timepoint 1 and UMPC Timepoint 1 and 4
Old_UO_CBCL_Names_T1 <- sprintf("Q264_%01d", seq(1:100))
Old_UPMC_CBCL_Names_T1_T4 <- sprintf("Q15.1_%01d", seq(1:100))

# Old names for UO Timepoint 2, UMPC Timepoints 2 and 3
Old_UO_CBCL_Names_T2 <- sprintf("Q368_%01d", seq(1:100))
Old_UPMC_CBCL_Names_T2_T3 <- sprintf("Q12.1_%01d", seq(1:100))

# Old names for UO Timepoint 3
Old_UO_CBCL_Names_T3 <- sprintf("Q534_%01d", seq(1:100))

# Old names for UO timepoint 4
Old_UO_CBCL_Names_T4 <- sprintf("Q828_%01d", seq(1:100))

# Replace UO column names (there may be errors from the CBCL TEXT question responses) 
setnames(UO_T1_CBCL, Old_UO_CBCL_Names_T1, New_CBCL_Names)
setnames(UO_T2_CBCL, Old_UO_CBCL_Names_T2, New_CBCL_Names)
setnames(UO_T3_CBCL, Old_UO_CBCL_Names_T3, New_CBCL_Names)
setnames(UO_T4_CBCL, Old_UO_CBCL_Names_T4, New_CBCL_Names)

# Replace UPMC column names (there may be errors from the CBCL TEXT question responses)
setnames(UPMC_T1_CBCL, Old_UPMC_CBCL_Names_T1_T4, New_CBCL_Names)
setnames(UPMC_T2_CBCL, Old_UPMC_CBCL_Names_T2_T3, New_CBCL_Names)
setnames(UPMC_T3_CBCL, Old_UPMC_CBCL_Names_T2_T3, New_CBCL_Names)
setnames(UPMC_T4_CBCL, Old_UPMC_CBCL_Names_T1_T4, New_CBCL_Names)

```

# Prep Sheet
Create prep sheet to begin transferring data into NDA format. Rename relevant GUID information to match NDA specifications. Finally, bind all timepoints into single CBCL Prep Sheet.
```{r Prep Sheet}
# Edit UO CBCL Time 1 - 4 to have only CBCL quesions and the FamID
UO_T1_CBCL <- select(UO_T1_CBCL, c(FamID = Q221, contains("cbcl")))
UO_T2_CBCL <- select(UO_T2_CBCL, c(FamID = Q116, contains("cbcl")))
UO_T3_CBCL <- select(UO_T3_CBCL, c(FamID = Q174, contains("cbcl")))
UO_T4_CBCL <- select(UO_T4_CBCL, c(FamID = Q203, contains("cbcl")))

# Edit UPMC CBCL Time 1 - 4 to have only CBCL quesions and the FamID
UPMC_T1_CBCL <- select(UPMC_T1_CBCL, c(FamID = Q1.2, contains("cbcl")))
UPMC_T2_CBCL <- select(UPMC_T2_CBCL, c(FamID = Q1.2, contains("cbcl")))
UPMC_T3_CBCL <- select(UPMC_T3_CBCL, c(FamID = Q1.2, contains("cbcl")))
UPMC_T4_CBCL <- select(UPMC_T4_CBCL, c(FamID = Q1.2, contains("cbcl")))

# Bind UO and UPMC CBCL Data By Timepoint
CBCL_T1 <- rbind(UO_T1_CBCL, UPMC_T1_CBCL)
CBCL_T2 <- rbind(UO_T2_CBCL, UPMC_T2_CBCL)
CBCL_T3 <- rbind(UO_T3_CBCL, UPMC_T3_CBCL)
CBCL_T4 <- rbind(UO_T4_CBCL, UPMC_T4_CBCL)

# Clean  Environment of intermediate calculations for question selection and column renaming
rm(UO_T1_CBCL, UO_T2_CBCL, UO_T3_CBCL, UO_T4_CBCL, UPMC_T1_CBCL, UPMC_T2_CBCL, UPMC_T3_CBCL, UPMC_T4_CBCL, 
   Old_UO_CBCL_Names_T1, Old_UO_CBCL_Names_T2, Old_UO_CBCL_Names_T3, Old_UO_CBCL_Names_T4, Old_UPMC_CBCL_Names_T1_T4, Old_UPMC_CBCL_Names_T2_T3)

# Create the Predigree data for each Timepoint
Pedigree_T1 <- select(Pedigree, FamID, child_guid, child_FamID = FamID_Child, child_sex = ChildGender, interview_age = ChildAge_T1, interview_date = Time1Date, GroupAssignment)
Pedigree_T2 <- select(Pedigree, FamID, child_guid, child_FamID = FamID_Child, child_sex = ChildGender, interview_age = ChildAge_T2, interview_date = Time2Date, GroupAssignment)
Pedigree_T3 <- select(Pedigree, FamID, child_guid, child_FamID = FamID_Child, child_sex = ChildGender, interview_age = ChildAge_T3, interview_date = Time3Date, GroupAssignment)
Pedigree_T4 <- select(Pedigree, FamID, child_guid, child_FamID = FamID_Child, child_sex = ChildGender, interview_age = ChildAge_T4, interview_date = Time4Date, GroupAssignment)

# Merge Pedigree data to CBCL Time Points
CBCL_T1 <- merge(Pedigree_T1, CBCL_T1, by = 'FamID')
CBCL_T2 <- merge(Pedigree_T2, CBCL_T2, by = 'FamID')
CBCL_T3 <- merge(Pedigree_T3, CBCL_T3, by = 'FamID')
CBCL_T4 <- merge(Pedigree_T4, CBCL_T4, by = 'FamID')

# Clean Environment of intermediate calculations for pedigree data
rm(Pedigree, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)

# Create Time Point coloumn in each CBCL Sheet and populate the cell with time point
CBCL_T1$timepoint <- "Time 1"
CBCL_T2$timepoint <- "Time 2"
CBCL_T3$timepoint <- "Time 3"
CBCL_T4$timepoint <- "Time 4"

# Bind all cbcl Time Points together creating the CBCL Prep sheet
CBCL_Prep <- rbind(CBCL_T1, CBCL_T2, CBCL_T3, CBCL_T4)

# Clean Environment of intermediate calculations for Prep sheet binding
rm(CBCL_T1, CBCL_T2, CBCL_T3, CBCL_T4)

```

# Re-code
Convert Likert Scale text input into numerical values then create a dataframe to place ID's that do not have 67% of their data present.(There's an issue this presents that I will have to deal with later)
```{r Re-code and 67% Rule}
# Recode text responses into numbers so they can be used in calculations
CBCL_Prep <- CBCL_Prep %>% 
  mutate_at(New_CBCL_Names,
            funs(recode(., "Not True (as far as you know)" = 0, 
                        "Somewhat or Sometimes True" = 1,
                        "Very True or Often True" = 2,.default = NaN)))

# Recode UPMC Group Assignment names to match UO Group Assignment names
CBCL_Prep <- CBCL_Prep %>% 
  mutate_at(c("GroupAssignment"),
            funs(recode(., "Assigned Group 3 (HC)" = "Healthy", 
                        'Assigned Group 2 (FSU)' = "NO DBT",
                        'Assigned Group 1 (DBT)' = "DBT")))

# Check NA percentage
CBCL_Prep$NACheck <- rowSums(is.na(select(CBCL_Prep, starts_with("srm"))))/ncol(dplyr::select(CBCL_Prep, starts_with("srm")))

# Drop people who are less than 67% & 100%
CBCL_Drop_67 <- CBCL_Prep[CBCL_Prep$NACheck > 0.67, ]
CBCL_Prep_67 <- CBCL_Prep[CBCL_Prep$NACheck <= 0.67, ]

CBCL_Drop_100 <- CBCL_Prep[CBCL_Prep$NACheck > 0, ]
CBCL_Prep_100 <- CBCL_Prep[CBCL_Prep$NACheck <= 0, ]

```

# Calculated Columns
Create sums column combining each individual measure. Separate caulculations are needed for the 67% and 100% Prep Sheet.
```{r calculated columns}
# Create calculated columns for 67% version of the Prep Sheet
# Creating calculated columns for "cbcl_er"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_er = rowSums(CBCL_Prep_67[, c("srm_cbcl_021", "srm_cbcl_046", "srm_cbcl_051", "srm_cbcl_079", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_092", 
                                                                   "srm_cbcl_097", "srm_cbcl_099")]),.after = "srm_cbcl_100")


# Creating calculated columns for "cbcl_ad"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_ad = rowSums(CBCL_Prep_67[, c("srm_cbcl_010", "srm_cbcl_033", "srm_cbcl_037", "srm_cbcl_043", "srm_cbcl_047", "srm_cbcl_068", "srm_cbcl_087", 
                                                                   "srm_cbcl_090")]),.after = "cbcl_er")


# Creating calculated columns for "cbcl_sc"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_sc = rowSums(CBCL_Prep_67[, c("srm_cbcl_001", "srm_cbcl_007", "srm_cbcl_012", "srm_cbcl_019", "srm_cbcl_024", "srm_cbcl_039", "srm_cbcl_045", 
                                                                   "srm_cbcl_052", "srm_cbcl_078", "srm_cbcl_086", "srm_cbcl_093")]),.after = "cbcl_ad")


# Creating calculated columns for "cbcl_w"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_w = rowSums(CBCL_Prep_67[, c("srm_cbcl_002", "srm_cbcl_004", "srm_cbcl_023", "srm_cbcl_062", "srm_cbcl_100", "srm_cbcl_070", "srm_cbcl_071", 
                                                                  "srm_cbcl_098")]),.after = "cbcl_sc")


# Creating calculated columns for "cbcl_sp"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_sp = rowSums(CBCL_Prep_67[, c("srm_cbcl_022", "srm_cbcl_038", "srm_cbcl_048", "srm_cbcl_064", "srm_cbcl_074",
                                                                   "srm_cbcl_084")]),.after = "cbcl_w")


# Creating calculated columns for "cbcl_ap"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_ap = rowSums(CBCL_Prep_67[, c("srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_056", "srm_cbcl_059",
                                                                   "srm_cbcl_095")]),.after = "cbcl_sp")


# Creating calculated columns for "cbcl_ab"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_ab = rowSums(CBCL_Prep_67[, c("srm_cbcl_008", "srm_cbcl_015", "srm_cbcl_016", "srm_cbcl_018", "srm_cbcl_020", "srm_cbcl_027", "srm_cbcl_029", 
                                                                   "srm_cbcl_035", "srm_cbcl_040", "srm_cbcl_042", "srm_cbcl_044", "srm_cbcl_053", "srm_cbcl_058", "srm_cbcl_066", 
                                                                   "srm_cbcl_069", "srm_cbcl_081", "srm_cbcl_085", "srm_cbcl_088", "srm_cbcl_096")]),.after = "cbcl_ap")


# Creating calculated columns for "cbcl_op"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_op = rowSums(CBCL_Prep_67[, c("srm_cbcl_003", "srm_cbcl_009", "srm_cbcl_011", "srm_cbcl_013", "srm_cbcl_014", "srm_cbcl_017", "srm_cbcl_025", 
                                                                   "srm_cbcl_026", "srm_cbcl_028", "srm_cbcl_030", "srm_cbcl_031", "srm_cbcl_032", "srm_cbcl_034", "srm_cbcl_036", 
                                                                   "srm_cbcl_041", "srm_cbcl_049", "srm_cbcl_050", "srm_cbcl_054", "srm_cbcl_055", "srm_cbcl_057", "srm_cbcl_060",
                                                                   "srm_cbcl_061", "srm_cbcl_063", "srm_cbcl_065", "srm_cbcl_072", "srm_cbcl_073", "srm_cbcl_075", "srm_cbcl_076",
                                                                   "srm_cbcl_077", "srm_cbcl_080", "srm_cbcl_089", "srm_cbcl_091", "srm_cbcl_094")]),.after = "cbcl_ab")


# Creating calculated columns for "cbcl_int"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_int = rowSums(CBCL_Prep_67[, c("srm_cbcl_021", "srm_cbcl_046", "srm_cbcl_051", "srm_cbcl_079", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_092", 
                                                                    "srm_cbcl_097", "srm_cbcl_099", "srm_cbcl_010", "srm_cbcl_033", "srm_cbcl_037", "srm_cbcl_043", "srm_cbcl_047", 
                                                                    "srm_cbcl_068", "srm_cbcl_087", "srm_cbcl_090", "srm_cbcl_001", "srm_cbcl_007", "srm_cbcl_012", "srm_cbcl_019",
                                                                    "srm_cbcl_024", "srm_cbcl_039", "srm_cbcl_045", "srm_cbcl_052", "srm_cbcl_078", "srm_cbcl_086", "srm_cbcl_093", 
                                                                    "srm_cbcl_002", "srm_cbcl_004", "srm_cbcl_023", "srm_cbcl_062", "srm_cbcl_067", "srm_cbcl_070", "srm_cbcl_071",
                                                                    "srm_cbcl_098")]),.after = "cbcl_op")


# Creating calculated columns for "cbcl_ext"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_ext = rowSums(CBCL_Prep_67[, c("srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_056", "srm_cbcl_059", "srm_cbcl_095", "srm_cbcl_008", "srm_cbcl_015",
                                                                    "srm_cbcl_016", "srm_cbcl_018", "srm_cbcl_020", "srm_cbcl_027", "srm_cbcl_029", "srm_cbcl_035", "srm_cbcl_040",
                                                                    "srm_cbcl_042", "srm_cbcl_044", "srm_cbcl_053", "srm_cbcl_058", "srm_cbcl_066", "srm_cbcl_069", "srm_cbcl_081",
                                                                    "srm_cbcl_085", "srm_cbcl_088", "srm_cbcl_096")]),.after = "cbcl_int")


# Creating calculated columns for "cbcl_total"
CBCL_Prep_67 <- add_column(CBCL_Prep_67, cbcl_total = rowSums(CBCL_Prep_67[, c("srm_cbcl_001", "srm_cbcl_002", "srm_cbcl_003", "srm_cbcl_004", "srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_007",
                                                                      "srm_cbcl_008", "srm_cbcl_009", "srm_cbcl_010", "srm_cbcl_011", "srm_cbcl_012", "srm_cbcl_013", "srm_cbcl_014",
                                                                      "srm_cbcl_015", "srm_cbcl_016", "srm_cbcl_017", "srm_cbcl_018", "srm_cbcl_019", "srm_cbcl_020", "srm_cbcl_021",
                                                                      "srm_cbcl_022", "srm_cbcl_023", "srm_cbcl_024", "srm_cbcl_025", "srm_cbcl_026", "srm_cbcl_027", "srm_cbcl_028",
                                                                      "srm_cbcl_029", "srm_cbcl_030", "srm_cbcl_031", "srm_cbcl_032", "srm_cbcl_033", "srm_cbcl_034", "srm_cbcl_035",
                                                                      "srm_cbcl_036", "srm_cbcl_037", "srm_cbcl_038", "srm_cbcl_039", "srm_cbcl_040", "srm_cbcl_041", "srm_cbcl_042",
                                                                      "srm_cbcl_043", "srm_cbcl_044", "srm_cbcl_045", "srm_cbcl_046", "srm_cbcl_047", "srm_cbcl_048", "srm_cbcl_049",
                                                                      "srm_cbcl_050", "srm_cbcl_051", "srm_cbcl_052", "srm_cbcl_053", "srm_cbcl_054", "srm_cbcl_055", "srm_cbcl_056",
                                                                      "srm_cbcl_057", "srm_cbcl_058", "srm_cbcl_059", "srm_cbcl_060", "srm_cbcl_061", "srm_cbcl_062", "srm_cbcl_063",
                                                                      "srm_cbcl_064", "srm_cbcl_065", "srm_cbcl_066", "srm_cbcl_067", "srm_cbcl_068", "srm_cbcl_069", "srm_cbcl_070",
                                                                      "srm_cbcl_071", "srm_cbcl_072", "srm_cbcl_073", "srm_cbcl_074", "srm_cbcl_075", "srm_cbcl_076", "srm_cbcl_077",
                                                                      "srm_cbcl_078", "srm_cbcl_079", "srm_cbcl_080", "srm_cbcl_081", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_084",
                                                                      "srm_cbcl_085", "srm_cbcl_086", "srm_cbcl_087", "srm_cbcl_088", "srm_cbcl_089", "srm_cbcl_090", "srm_cbcl_091",
                                                                      "srm_cbcl_092", "srm_cbcl_093", "srm_cbcl_094", "srm_cbcl_095", "srm_cbcl_096", "srm_cbcl_097", "srm_cbcl_098",
                                                                      "srm_cbcl_099")]),.after = "cbcl_ext")

#--------------------------------------------------------------------------------------------------------------

# Create calculated columns for 100% version of the Prep Sheet
# Creating calculated columns for "cbcl_er"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_er = rowSums(CBCL_Prep_100[, c("srm_cbcl_021", "srm_cbcl_046", "srm_cbcl_051", "srm_cbcl_079", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_092", 
                                                                   "srm_cbcl_097", "srm_cbcl_099")]),.after = "srm_cbcl_100")


# Creating calculated columns for "cbcl_ad"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_ad = rowSums(CBCL_Prep_100[, c("srm_cbcl_010", "srm_cbcl_033", "srm_cbcl_037", "srm_cbcl_043", "srm_cbcl_047", "srm_cbcl_068", "srm_cbcl_087", 
                                                                   "srm_cbcl_090")]),.after = "cbcl_er")


# Creating calculated columns for "cbcl_sc"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_sc = rowSums(CBCL_Prep_100[, c("srm_cbcl_001", "srm_cbcl_007", "srm_cbcl_012", "srm_cbcl_019", "srm_cbcl_024", "srm_cbcl_039", "srm_cbcl_045", 
                                                                   "srm_cbcl_052", "srm_cbcl_078", "srm_cbcl_086", "srm_cbcl_093")]),.after = "cbcl_ad")


# Creating calculated columns for "cbcl_w"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_w = rowSums(CBCL_Prep_100[, c("srm_cbcl_002", "srm_cbcl_004", "srm_cbcl_023", "srm_cbcl_062", "srm_cbcl_100", "srm_cbcl_070", "srm_cbcl_071", 
                                                                  "srm_cbcl_098")]),.after = "cbcl_sc")


# Creating calculated columns for "cbcl_sp"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_sp = rowSums(CBCL_Prep_100[, c("srm_cbcl_022", "srm_cbcl_038", "srm_cbcl_048", "srm_cbcl_064", "srm_cbcl_074",
                                                                   "srm_cbcl_084")]),.after = "cbcl_w")


# Creating calculated columns for "cbcl_ap"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_ap = rowSums(CBCL_Prep_100[, c("srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_056", "srm_cbcl_059",
                                                                   "srm_cbcl_095")]),.after = "cbcl_sp")


# Creating calculated columns for "cbcl_ab"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_ab = rowSums(CBCL_Prep_100[, c("srm_cbcl_008", "srm_cbcl_015", "srm_cbcl_016", "srm_cbcl_018", "srm_cbcl_020", "srm_cbcl_027", "srm_cbcl_029", 
                                                                   "srm_cbcl_035", "srm_cbcl_040", "srm_cbcl_042", "srm_cbcl_044", "srm_cbcl_053", "srm_cbcl_058", "srm_cbcl_066", 
                                                                   "srm_cbcl_069", "srm_cbcl_081", "srm_cbcl_085", "srm_cbcl_088", "srm_cbcl_096")]),.after = "cbcl_ap")


# Creating calculated columns for "cbcl_op"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_op = rowSums(CBCL_Prep_100[, c("srm_cbcl_003", "srm_cbcl_009", "srm_cbcl_011", "srm_cbcl_013", "srm_cbcl_014", "srm_cbcl_017", "srm_cbcl_025", 
                                                                   "srm_cbcl_026", "srm_cbcl_028", "srm_cbcl_030", "srm_cbcl_031", "srm_cbcl_032", "srm_cbcl_034", "srm_cbcl_036", 
                                                                   "srm_cbcl_041", "srm_cbcl_049", "srm_cbcl_050", "srm_cbcl_054", "srm_cbcl_055", "srm_cbcl_057", "srm_cbcl_060",
                                                                   "srm_cbcl_061", "srm_cbcl_063", "srm_cbcl_065", "srm_cbcl_072", "srm_cbcl_073", "srm_cbcl_075", "srm_cbcl_076",
                                                                   "srm_cbcl_077", "srm_cbcl_080", "srm_cbcl_089", "srm_cbcl_091", "srm_cbcl_094")]),.after = "cbcl_ab")


# Creating calculated columns for "cbcl_int"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_int = rowSums(CBCL_Prep_100[, c("srm_cbcl_021", "srm_cbcl_046", "srm_cbcl_051", "srm_cbcl_079", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_092", 
                                                                    "srm_cbcl_097", "srm_cbcl_099", "srm_cbcl_010", "srm_cbcl_033", "srm_cbcl_037", "srm_cbcl_043", "srm_cbcl_047", 
                                                                    "srm_cbcl_068", "srm_cbcl_087", "srm_cbcl_090", "srm_cbcl_001", "srm_cbcl_007", "srm_cbcl_012", "srm_cbcl_019",
                                                                    "srm_cbcl_024", "srm_cbcl_039", "srm_cbcl_045", "srm_cbcl_052", "srm_cbcl_078", "srm_cbcl_086", "srm_cbcl_093", 
                                                                    "srm_cbcl_002", "srm_cbcl_004", "srm_cbcl_023", "srm_cbcl_062", "srm_cbcl_067", "srm_cbcl_070", "srm_cbcl_071",
                                                                    "srm_cbcl_098")]),.after = "cbcl_op")


# Creating calculated columns for "cbcl_ext"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_ext = rowSums(CBCL_Prep_100[, c("srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_056", "srm_cbcl_059", "srm_cbcl_095", "srm_cbcl_008", "srm_cbcl_015",
                                                                    "srm_cbcl_016", "srm_cbcl_018", "srm_cbcl_020", "srm_cbcl_027", "srm_cbcl_029", "srm_cbcl_035", "srm_cbcl_040",
                                                                    "srm_cbcl_042", "srm_cbcl_044", "srm_cbcl_053", "srm_cbcl_058", "srm_cbcl_066", "srm_cbcl_069", "srm_cbcl_081",
                                                                    "srm_cbcl_085", "srm_cbcl_088", "srm_cbcl_096")]),.after = "cbcl_int")


# Creating calculated columns for "cbcl_total"
CBCL_Prep_100 <- add_column(CBCL_Prep_100, cbcl_total = rowSums(CBCL_Prep_100[, c("srm_cbcl_001", "srm_cbcl_002", "srm_cbcl_003", "srm_cbcl_004", "srm_cbcl_005", "srm_cbcl_006", "srm_cbcl_007",
                                                                      "srm_cbcl_008", "srm_cbcl_009", "srm_cbcl_010", "srm_cbcl_011", "srm_cbcl_012", "srm_cbcl_013", "srm_cbcl_014",
                                                                      "srm_cbcl_015", "srm_cbcl_016", "srm_cbcl_017", "srm_cbcl_018", "srm_cbcl_019", "srm_cbcl_020", "srm_cbcl_021",
                                                                      "srm_cbcl_022", "srm_cbcl_023", "srm_cbcl_024", "srm_cbcl_025", "srm_cbcl_026", "srm_cbcl_027", "srm_cbcl_028",
                                                                      "srm_cbcl_029", "srm_cbcl_030", "srm_cbcl_031", "srm_cbcl_032", "srm_cbcl_033", "srm_cbcl_034", "srm_cbcl_035",
                                                                      "srm_cbcl_036", "srm_cbcl_037", "srm_cbcl_038", "srm_cbcl_039", "srm_cbcl_040", "srm_cbcl_041", "srm_cbcl_042",
                                                                      "srm_cbcl_043", "srm_cbcl_044", "srm_cbcl_045", "srm_cbcl_046", "srm_cbcl_047", "srm_cbcl_048", "srm_cbcl_049",
                                                                      "srm_cbcl_050", "srm_cbcl_051", "srm_cbcl_052", "srm_cbcl_053", "srm_cbcl_054", "srm_cbcl_055", "srm_cbcl_056",
                                                                      "srm_cbcl_057", "srm_cbcl_058", "srm_cbcl_059", "srm_cbcl_060", "srm_cbcl_061", "srm_cbcl_062", "srm_cbcl_063",
                                                                      "srm_cbcl_064", "srm_cbcl_065", "srm_cbcl_066", "srm_cbcl_067", "srm_cbcl_068", "srm_cbcl_069", "srm_cbcl_070",
                                                                      "srm_cbcl_071", "srm_cbcl_072", "srm_cbcl_073", "srm_cbcl_074", "srm_cbcl_075", "srm_cbcl_076", "srm_cbcl_077",
                                                                      "srm_cbcl_078", "srm_cbcl_079", "srm_cbcl_080", "srm_cbcl_081", "srm_cbcl_082", "srm_cbcl_083", "srm_cbcl_084",
                                                                      "srm_cbcl_085", "srm_cbcl_086", "srm_cbcl_087", "srm_cbcl_088", "srm_cbcl_089", "srm_cbcl_090", "srm_cbcl_091",
                                                                      "srm_cbcl_092", "srm_cbcl_093", "srm_cbcl_094", "srm_cbcl_095", "srm_cbcl_096", "srm_cbcl_097", "srm_cbcl_098",
                                                                      "srm_cbcl_099")]),.after = "cbcl_ext")

```

# NDA Sheet
Re-name CBCL Prep Sheet columns to match NDA specifications. 
```{r NDA Sheet}
# Create NDA prep sheet
# Select all the needed columns from CBCL_Prep sheet
NDA_CBCL_Prep <- select(CBCL_Prep, c(subjectkey = child_guid, src_subject_id = child_FamID, sex = child_sex ,interview_age, interview_date, starts_with("srm")))

# Create NDA structure column names, they are unique and without a pattern so they must be made manually 
NDA_CBCL_Names <- paste(c("cbcl56a", "cbcl1", "cbcl_nt", "cbcl_eye", "cbcl8", "cbcl10", "cbcl_out", "cbcl_wait", "cbcl_chew", "cbcl11", "cbcl_help", "cbcl49", "cbcl14", "cbcl15", "cbcl_defiant", "cbcl_dem", "cbcl20", 
                         "cbcl21", "cbcl_diar", "cbcl_disob", "cbcl_dist", "cbcl_alonsleep", "cbcl_answer", "cbcl24", "cbcl25", "cbcl_fun", "cbcl26", "cbcl_home", "cbcl_frust", "cbcl27", "cbcl_eat", "cbcl29", "cbcl_feel", "cbcl36", 
                         "cbcl37", "cbcl_every", "cbcl_upset", "cbcl_troubsleep", "cbcl56b", "cbcl_hit", "cbcl_breath", "cbcl_hurt", "cbcl_unhap", "cbcl_angry", "cbcl56c", "cbcl46", "cbcl45", "cbcl47", "cbcl53", "cbcl54", "cbcl_panic",
                         "cbcl_bow", "cbcl57", "cbcl58", "cbcl60", "cbcl62", "cbcl56d", "cbcl_punish", "cbcl_shift", "cbcl56e", "cbcl_reat", "cbcl_play", "cbcl_rock", "cbcl_bed", "cbcl_toil", "cbcl68", "cbcl_aff", "cbcl71", "cbcl_selfish",
                         "cbcl_littleaf", "cbcl_inter", "cbcl_fear", "cbcl75", "cbcl76", "cbcl_smear", "cbcl79", "cbcl_stares", "cbcl56f", "cbcl_sad", "cbcl84", "cbcl86", "cbcl87", "cbcl88", "cbcl_crie", "cbcl95", "cbcl_clean", "cbcl50",
                         "cbcl_uncoop", "cbcl102", "cbcl103", "cbcl104", "cbcl_people", "cbcl56g", "cbcl_wake", "cbcl_wand", "cbcl19", "cbcl109", "cbcl_withdr", "cbcl112", "cbcl113a"))

# Change names in the NDA_CBCL_Prep to match the NDA structure column names
setnames(NDA_CBCL_Prep, New_CBCL_Names, NDA_CBCL_Names)

# Make an empty row in the NDA sheet for compatibility (to avoid some potential errors)
NDA_CBCL[1,] <- NA

# Combine NDA CBCL Prep sheet with the NDA structure
NDA_CBCL <- bind_rows(NDA_CBCL,NDA_CBCL_Prep)

# Recreate first line in orignial NDA file
# Make an empty row, with same number of column in NDA_CBCL, as first line of NDA sheet
# ncol(NDA_CBCL)  is number of columns in NDA_CBCL
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_CBCL))

# assign the first cell in first_line as cbcl1_5 which is the first cell in orignial NDA structure
first_line[,1] <- "cbcl1_5"

# assign the second cell in first_line as "1"
first_line[,2] <- "1"

# Create a new file in folder called cbcl1_5.csv, and put first line into this file
# cbcl1_5.csv file will be saved into same folder as this current r script
write.table(first_line, file = "cbcl1_5.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = FALSE, row.names = FALSE)

# Append data in NDA_CBCL into cbcl1_5.csv file 
write.table(NDA_CBCL, file = 'cbcl1_5.csv', sep = ",", append = TRUE, na = "", quote = FALSE, row.names = FALSE)

# Clean environment of intermediate calculations for NDA structure
rm(NDA_CBCL_Prep, NDA_CBCL_Names, UO, UPMC, first_line, New_CBCL_Names, Timepoint_names)

```

# All Data Table
Create descriptive means table. (This all data table no longer functions but isn't used regardless)
```{r All Data Table, echo=FALSE}
# Select needed columns
Progress <- select(CBCL_Prep, c(FamID, GroupAssignment, timepoint, cbcl_ext, cbcl_int, cbcl_total, starts_with("srm")))

# Change FamId as character and assign it to the ID variable 
ID <- c(as.character(Progress$FamID))

# Add "Site" column to Progress, if an ID start with 9 then the site is UO, otherwise it is UPMC
Progress$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# Group by GroupAssignment  and Timepoint, and calculate the Group Mean
# Grouping & calculation for CBCL total
Progress_Total_Mean <- Progress %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(TotalMean = mean(cbcl_total,na.rm = T),count = n())

# Grouping & calculation for CBCL Int
Progress_Int_Mean <- Progress %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(IntMean = mean(cbcl_int,na.rm = T),count = n())

# Grouping & calculation for CBCL Ext
Progress_Ext_Mean <- Progress %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(ExtMean = mean(cbcl_ext,na.rm = T),count = n())

# Merge Total, Int, and Ext calculations
Progress_Mean <- merge(Progress_Int_Mean, Progress_Ext_Mean)
Progress_Mean <- merge(Progress_Mean, Progress_Total_Mean)

# Select only UO Mean to have UO data separate
UO <- Progress_Mean[Progress_Mean$site == "UO",]

# Select only UPMC Mean to have UMPC data separate
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Calculate both site mean between UO and UMPC
# Grouping & calculation for CBCL total
Progress_Total_Mean_Both <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_TotalMean" = mean(cbcl_total,na.rm = T),n = n())

# Grouping & calculation for CBCL Int
Progress_Int_Mean_Both <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_IntMean" = mean(cbcl_int,na.rm = T),n = n())

# Grouping & calculation for CBCL Ext
Progress_Ext_Mean_Both <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_ExtMean" = mean(cbcl_ext,na.rm = T),n = n())

# Merge both site Total, Int, and Ext calculations 
Both_Site_Mean <- merge(Progress_Int_Mean_Both, Progress_Ext_Mean_Both)
Both_Site_Mean <- merge(Both_Site_Mean, Progress_Total_Mean_Both)

# Change GroupMean Column names according to site and subscale
colnames(UO)[colnames(UO) == "TotalMean"] = "UO_CBCL_TotalMean"
colnames(UO)[colnames(UO) == "IntMean"] = "UO_CBCL_IntMean"
colnames(UO)[colnames(UO) == "ExtMean"] = "UO_CBCL_ExtMean"
colnames(UPMC)[colnames(UPMC) == "TotalMean"] = "UPMC_CBCL_TotalMean"
colnames(UPMC)[colnames(UPMC) == "IntMean"] = "UPMC_CBCL_IntMean"
colnames(UPMC)[colnames(UPMC) == "ExtMean"] = "UPMC_CBCL_ExtMean"

# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_CBCL_TotalMean","UO_CBCL_IntMean", "UO_CBCL_ExtMean")],UPMC[,c("UPMC_CBCL_TotalMean", "UPMC_CBCL_IntMean", "UPMC_CBCL_ExtMean")],Both_Site_Mean[,c("BothSite_CBCL_TotalMean", "BothSite_CBCL_IntMean", "BothSite_CBCL_ExtMean","n", "GroupAssignment")])

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

# Reorder Mean_Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint columns
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column names
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Table output ----------
# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = T) %>%
  add_header_above(c(" " = 1, "Controls Group means" = 4, "FSU Group means" = 4, "DBT Group means" = 4)) %>%
  add_header_above(c("CBCL Mean Table" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")

# Clean Environment of intermediate calculations for "all data" table.
rm(Progress, Progress_Ext_Mean, Progress_Ext_Mean_Both, Progress_Int_Mean, Progress_Int_Mean_Both, Progress_Mean, Progress_Total_Mean, Progress_Total_Mean_Both, Both_Site_Mean)

```

# 67% Data Table
Create descriptives table for only ID's that have 67% of their data.
```{r 67% Data Table, echo=FALSE}
# Select needed column
Progress_67 <- select(CBCL_Prep_67, c(FamID, GroupAssignment, timepoint, cbcl_ext, cbcl_int, cbcl_total, starts_with("srm")))

# Change FamId as character and assign it to the ID variable  
ID <- c(as.character(Progress_67$FamID))

# Add "Site" column to Progress, if an ID start with 9 then the site is UO, otherwise it is UPMC
Progress_67$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# Group by GroupAssignment  and Timepoint, and calculate the Group Mean
# Grouping & calculation for CBCL total
Progress_67_Total_Mean <- Progress_67 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(TotalMean = mean(cbcl_total,na.rm = T),count = n())

# Grouping & calculation for CBCL Int
Progress_67_Int_Mean <- Progress_67 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(IntMean = mean(cbcl_int,na.rm = T),count = n())

# Grouping & calculation for CBCL Ext
Progress_67_Ext_Mean <- Progress_67 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(ExtMean = mean(cbcl_ext,na.rm = T),count = n())

# Merge Total, Int, and Ext calculations
Progress_67_Mean <- merge(Progress_67_Int_Mean, Progress_67_Ext_Mean)
Progress_67_Mean <- merge(Progress_67_Mean, Progress_67_Total_Mean)

# Select only UO Mean to have UO data separate
UO <- Progress_67_Mean[Progress_67_Mean$site == "UO",]

# Select only UMPC Mean to have UMPC data separate
UPMC <- Progress_67_Mean[Progress_67_Mean$site == "UPMC",]

# Calculate both site mean between UO and UMPC
# Grouping & calculation for CBCL total
Progress_67_Total_Mean_Both <- Progress_67 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_TotalMean" = mean(cbcl_total,na.rm = T),n = n())

# Grouping & calculation for CBCL Int
Progress_67_Int_Mean_Both <- Progress_67 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_IntMean" = mean(cbcl_int,na.rm = T),n = n())

# Grouping & calculation for CBCL Ext
Progress_67_Ext_Mean_Both <- Progress_67 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_ExtMean" = mean(cbcl_ext,na.rm = T),n = n())

# Merge both site Total, Ext, and Int calculations
Both_Site_Mean_67 <- merge(Progress_67_Int_Mean_Both, Progress_67_Ext_Mean_Both)
Both_Site_Mean_67 <- merge(Both_Site_Mean_67, Progress_67_Total_Mean_Both)

# Change GroupMean Column names according to site and subscale
colnames(UO)[colnames(UO) == "TotalMean"] = "UO_CBCL_TotalMean"
colnames(UO)[colnames(UO) == "IntMean"] = "UO_CBCL_IntMean"
colnames(UO)[colnames(UO) == "ExtMean"] = "UO_CBCL_ExtMean"
colnames(UPMC)[colnames(UPMC) == "TotalMean"] = "UPMC_CBCL_TotalMean"
colnames(UPMC)[colnames(UPMC) == "IntMean"] = "UPMC_CBCL_IntMean"
colnames(UPMC)[colnames(UPMC) == "ExtMean"] = "UPMC_CBCL_ExtMean"


# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_CBCL_TotalMean","UO_CBCL_IntMean", "UO_CBCL_ExtMean")],UPMC[,c("UPMC_CBCL_TotalMean", "UPMC_CBCL_IntMean", "UPMC_CBCL_ExtMean")],Both_Site_Mean_67[,c("BothSite_CBCL_TotalMean", "BothSite_CBCL_IntMean", "BothSite_CBCL_ExtMean","n", "GroupAssignment")])


# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

# Reorder Mean_Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint columns
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column names 
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Table output ----------
# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = T) %>%
  add_header_above(c(" " = 1, "Controls Group means" = 4, "FSU Group means" = 4, "DBT Group means" = 4)) %>%
  add_header_above(c("CBCL Mean Table (67% NA Check)" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")

# Clean Environment of intermediate calculations for 67% table
rm(Progress_67, Progress_67_Ext_Mean_Both, Progress_67_Int_Mean_Both, Progress_67_Total_Mean_Both, Progress_67_Mean, Progress_67_Ext_Mean, Progress_67_Int_Mean, Progress_67_Total_Mean, Both_Site_Mean_67, ID)

```

# 100% Table
Create descriptives table for only ID's that have 100% of their data.
```{r 100% Data Table, echo=FALSE}
# Select needed column
Progress_100 <- select(CBCL_Prep_100, c(FamID, GroupAssignment, timepoint, cbcl_ext, cbcl_int, cbcl_total, starts_with("srm")))

# Change FamId as character and assign it to the ID variable 
ID <- c(as.character(Progress_100$FamID))

# Add "Site" column to Progress, if an ID start with 9 then the site is UO, otherwise it is UPMC
Progress_100$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# Group by GroupAssignment  and Timepoint, and calculate the Group Mean
# Grouping & calculation for CBCL total
Progress_100_Total_Mean <- Progress_100 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(TotalMean = mean(cbcl_total,na.rm = T),count = n())

# Grouping & calculation for CBCL Int
Progress_100_Int_Mean <- Progress_100 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(IntMean = mean(cbcl_int,na.rm = T),count = n())

# Grouping & calculation for CBCL Ext
Progress_100_Ext_Mean <- Progress_100 %>%
  group_by(GroupAssignment,timepoint,site) %>%
  summarise(ExtMean = mean(cbcl_ext,na.rm = T),count = n())

# Merge Total, Int, and Ext calculations
Progress_100_Mean <- merge(Progress_100_Int_Mean, Progress_100_Ext_Mean)
Progress_100_Mean <- merge(Progress_100_Mean, Progress_100_Total_Mean)

# Select only UO Mean to have UO data separate
UO <- Progress_100_Mean[Progress_100_Mean$site == "UO",]

# Select only UMPC Mean to have UMPC data separate
UPMC <- Progress_100_Mean[Progress_100_Mean$site == "UPMC",]

# Calculate both site mean between UO and UMPC
# Grouping & calculation for CBCL total
Progress_100_Total_Mean_Both <- Progress_100 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_TotalMean" = mean(cbcl_total,na.rm = T),n = n())

# Grouping & calculation for CBCL Int
Progress_100_Int_Mean_Both <- Progress_100 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_IntMean" = mean(cbcl_int,na.rm = T),n = n())

# Grouping & calculation for CBCL Ext
Progress_100_Ext_Mean_Both <- Progress_100 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise("BothSite_CBCL_ExtMean" = mean(cbcl_ext,na.rm = T),n = n())

# Merge both site Total, Int, and Ext calculations
Both_Site_Mean_100 <- merge(Progress_100_Int_Mean_Both, Progress_100_Ext_Mean_Both)
Both_Site_Mean_100 <- merge(Both_Site_Mean_100, Progress_100_Total_Mean_Both)

# Change GroupMean Column names according to site and subscale
colnames(UO)[colnames(UO) == "TotalMean"] = "UO_CBCL_TotalMean"
colnames(UO)[colnames(UO) == "IntMean"] = "UO_CBCL_IntMean"
colnames(UO)[colnames(UO) == "ExtMean"] = "UO_CBCL_ExtMean"
colnames(UPMC)[colnames(UPMC) == "TotalMean"] = "UPMC_CBCL_TotalMean"
colnames(UPMC)[colnames(UPMC) == "IntMean"] = "UPMC_CBCL_IntMean"
colnames(UPMC)[colnames(UPMC) == "ExtMean"] = "UPMC_CBCL_ExtMean"

# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_CBCL_TotalMean","UO_CBCL_IntMean", "UO_CBCL_ExtMean")],UPMC[,c("UPMC_CBCL_TotalMean", "UPMC_CBCL_IntMean", "UPMC_CBCL_ExtMean")],Both_Site_Mean_100[,c("BothSite_CBCL_TotalMean", "BothSite_CBCL_IntMean", "BothSite_CBCL_ExtMean","n", "GroupAssignment")])


# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

# Reorder Mean_Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint columns
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column names
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Table output ----------
# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = T) %>%
  add_header_above(c(" " = 1, "Controls Group means" = 4, "FSU Group means" = 4, "DBT Group means" = 4)) %>%
  add_header_above(c("CBCL Mean Table (100% NA Check)" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")

# Clean Environment of intermediate calculations for 100% table. 
rm(Progress_100, Progress_100_Ext_Mean_Both, Progress_100_Int_Mean_Both, Progress_100_Total_Mean_Both, Progress_100_Mean, Progress_100_Ext_Mean, Progress_100_Int_Mean, Progress_100_Total_Mean, Both_Site_Mean_100, ID)

```

# N Table
Create table for participant numbers. (Currently unused/unfinished)
```{r number table, include = T}

# Ignore all, incomplete


# Orig
ID <- c(as.character(cbcl_Prep$FamID))
cbcl_Prep$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")
N_org <- cbcl_Prep %>%
  group_by(timepoint, site, GroupAssignment) %>% 
  summarise(n_orig = n())


# 67%
ID <- c(as.character(cbcl_Prep_67$FamID))
cbcl_Prep_67$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")
N67 <- cbcl_Prep_67 %>%
  group_by(timepoint, site, GroupAssignment) %>% 
  summarise(n_67 = n())

# 100%
ID <- c(as.character(cbcl_Prep_100$FamID))
cbcl_Prep_100$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")
N100 <- cbcl_Prep_100 %>%
  group_by(timepoint, site, GroupAssignment) %>% 
  summarise(n_100 = n())

N <- cbind(N_org, N67, N100)
N <- N[,-c(5,6,7,9, 10, 11)]
N <- data.frame(t(N))

```