---
title: "WCCL"
author: "Kyle Murray"
date: "11/--/2020"
output: html_document
---
# Setup 
Loading library, set knitr and scientific notation
```{r Setup}
# Loading library 
library(dplyr)
library(tidyverse)
library(data.table)
library(kableExtra)
library(knitr)

# Settings for knit the whole document 
# Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
knitr::opts_chunk$set(echo = TRUE)

# Scientific notation, round up to 3 digits
options(digits = 3)
```
# Import
Empty Environment, Import Measurement, Pedigree data and NDA structure

```{r Import}
# Empty global environment
rm(list = ls())

# Import Pedigree and NDA structure
Pedigree <- read.csv("Reference_Pedigree.csv")
NDA_WCCL <- read.csv("dbt_wccl01_template.csv", skip = 1)

# Import UO and UPMC files 
UO_T1_WCCL <- read.csv("UO_T1_Qualtrics.csv", stringsAsFactors = FALSE)
UO_T2_WCCL <- read.csv("UO_T2_Qualtrics.csv", stringsAsFactors = FALSE)
UO_T3_WCCL <- read.csv("UO_T3_Qualtrics.csv", stringsAsFactors = FALSE)
UO_T4_WCCL <- read.csv("UO_T4_Qualtrics.csv", stringsAsFactors = FALSE)

UPMC_T1_WCCL <- read.csv("UPMC_T1_WCCL.csv", stringsAsFactors = FALSE)
UPMC_T2_WCCL <- read.csv("UPMC_T2_WCCL.csv", stringsAsFactors = FALSE)
UPMC_T3_WCCL <- read.csv("UPMC_T3_WCCL.csv", stringsAsFactors = FALSE)
UPMC_T4_WCCL <- read.csv("UPMC_T4_WCCL.csv", stringsAsFactors = FALSE)
```
# Rename Columns
Rename questions numbers to self-report measure scale items. Then, take each scale measure from both sites and combine them by timepoint.

```{r Rename Columns}
# Create new variable names 
wccl <- "srm_wccl"
num_items <- seq(1:59)
new_WCCL_names <- paste(wccl, num_items, sep = "_")
UO_Q155 <- "Q155"
old_UO_WCCL_names <- paste(UO_Q155, num_items, sep = "_")

# Replace old UO variable names with newly created names
setnames(UO_T1_WCCL, old_UO_WCCL_names, new_WCCL_names)
setnames(UO_T2_WCCL, old_UO_WCCL_names, new_WCCL_names)
setnames(UO_T3_WCCL, old_UO_WCCL_names, new_WCCL_names)
setnames(UO_T4_WCCL, old_UO_WCCL_names, new_WCCL_names)

# Replace old UPMC variable names with newly created names
UPMC_Q5 <- "Q5.1"
old_UPMC_WCCL_names <- paste(UPMC_Q5, num_items, sep = "_")
setnames(UPMC_T1_WCCL, old_UPMC_WCCL_names, new_WCCL_names)
setnames(UPMC_T2_WCCL, old_UPMC_WCCL_names, new_WCCL_names)
setnames(UPMC_T3_WCCL, old_UPMC_WCCL_names, new_WCCL_names)
setnames(UPMC_T4_WCCL, old_UPMC_WCCL_names, new_WCCL_names)

# edit UO WCCL time 1-4 to have only WCCL questions and fam ID 
UO_T1_WCCL <- select(UO_T1_WCCL, c(FamID=Q221, contains(wccl)))
UO_T2_WCCL <- select(UO_T2_WCCL, c(FamID=Q116, contains(wccl)))
UO_T3_WCCL <- select(UO_T3_WCCL, c(FamID=Q174, contains(wccl)))
UO_T4_WCCL <- select(UO_T4_WCCL, c(FamID=Q203, contains(wccl)))

# Edit UPMC T1-4 so only WCCL and FamID are left
UPMC_T1_WCCL <- select(UPMC_T1_WCCL, c(FamID=Q1.2, contains(wccl)))
UPMC_T2_WCCL <- select(UPMC_T2_WCCL, c(FamID=Q1.2, contains(wccl)))
UPMC_T3_WCCL <- select(UPMC_T3_WCCL, c(FamID=Q1.2, contains(wccl)))
UPMC_T4_WCCL <- select(UPMC_T4_WCCL, c(FamID=Q1.2, contains(wccl)))

# Binding UPMC And UO by time point
WCCL_T1 <- rbind(UO_T1_WCCL, UPMC_T1_WCCL)
WCCL_T2 <- rbind(UO_T2_WCCL, UPMC_T2_WCCL)
WCCL_T3 <- rbind(UO_T3_WCCL, UPMC_T3_WCCL)
WCCL_T4 <- rbind(UO_T4_WCCL, UPMC_T4_WCCL)
```
# Prep Sheet
Create prep sheet to begin transferring data into NDA format. Rename relevant GUID information to match NDA specifications. Finally, bind all timepoints into single WCCL Prep Sheet.

```{r Prep Sheet}
# Select relevant pedigree information, rename as needed. (Include GroupAssignment for treatment progress calculation.)
Pedigree_T1 <- select(Pedigree, FamID, mother_FamID = FamID_Mother, mom_guid, mother_sex = MomGender, interview_date = Time1Date, interview_age = MomAge_T1, GroupAssignment)
Pedigree_T2 <- select(Pedigree, FamID, mother_FamID = FamID_Mother, mom_guid, mother_sex = MomGender, interview_date = Time2Date, interview_age = MomAge_T2, GroupAssignment)
Pedigree_T3 <- select(Pedigree, FamID, mother_FamID = FamID_Mother, mom_guid, mother_sex = MomGender, interview_date = Time3Date, interview_age = MomAge_T3, GroupAssignment)
Pedigree_T4 <- select(Pedigree, FamID, mother_FamID = FamID_Mother, mom_guid, mother_sex = MomGender, interview_date = Time4Date, interview_age = MomAge_T4, GroupAssignment)

# merge Pedigree and WCCL by time point
WCCL_T1 <- merge(Pedigree_T1, WCCL_T1, by = 'FamID')
WCCL_T2 <- merge(Pedigree_T2, WCCL_T2, by = 'FamID')
WCCL_T3 <- merge(Pedigree_T3, WCCL_T3, by = 'FamID')
WCCL_T4 <- merge(Pedigree_T4, WCCL_T4, by = 'FamID')

# add time point column/populate with corresponding time point 
WCCL_T1$Timepoint <- "Time 1"
WCCL_T2$Timepoint <- "Time 2"
WCCL_T3$Timepoint <- "Time 3"
WCCL_T4$Timepoint <- "Time 4"

# Create WCCL_Prep and merge datasets 
WCCL_Prep <- rbind(WCCL_T1, WCCL_T2, WCCL_T3, WCCL_T4)

# Change gender to F instead of false
WCCL_Prep$mother_sex <- "F"

# Clean Global Environment
rm(UO_T1_WCCL, UO_T2_WCCL, UO_T3_WCCL, UO_T4_WCCL, UPMC_T1_WCCL, UPMC_T2_WCCL, UPMC_T3_WCCL, UPMC_T4_WCCL, Pedigree, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4, WCCL_T1, WCCL_T2, WCCL_T3, WCCL_T4)
```
# Re-code and 67% Rule
Convert Likert Scale text input into numerical values then create a dataframe to place ID's that do not have 67% of their data present.

```{r Recode}
# Recode Text to Integers
WCCL_Prep <- WCCL_Prep %>% mutate_at(new_WCCL_names,funs(recode(., '0 Never Used' = 0, '1 Rarely Used' = 1, '2 Sometimes Used' = 2, '3 Regularly Used' = 3,.default = NaN)))

# Change Numbers to Numeric values
WCCL_Prep[,8:59] <- sapply(WCCL_Prep[,8:59],as.numeric)

WCCL_Prep <- WCCL_Prep %>% 
  mutate_at(c("GroupAssignment"),
            funs(recode(., "Assigned Group 3 (HC)" = "Healthy", 
                        'Assigned Group 2 (FSU)' = "NO DBT",
                        'Assigned Group 1 (DBT)' = "DBT")))
```

```{r Calculated Columns}
# Items for SU
SU <- colnames(select(WCCL_Prep, c("srm_wccl_1", "srm_wccl_2", "srm_wccl_4", "srm_wccl_6", "srm_wccl_9", "srm_wccl_10", "srm_wccl_11", "srm_wccl_13", "srm_wccl_16", "srm_wccl_18", "srm_wccl_19", "srm_wccl_21", "srm_wccl_22", "srm_wccl_23", "srm_wccl_26", "srm_wccl_27", "srm_wccl_29", "srm_wccl_31", "srm_wccl_33", "srm_wccl_34", "srm_wccl_35", "srm_wccl_36", "srm_wccl_38", "srm_wccl_39", "srm_wccl_40", "srm_wccl_42", "srm_wccl_43", "srm_wccl_44", "srm_wccl_47", "srm_wccl_49", "srm_wccl_50", "srm_wccl_51", "srm_wccl_53", "srm_wccl_54", "srm_wccl_56", "srm_wccl_57", "srm_wccl_58", "srm_wccl_59")))

# Items for GSC
GSC <- colnames(select(WCCL_Prep, c("srm_wccl_3", "srm_wccl_5", "srm_wccl_8", "srm_wccl_12", "srm_wccl_14", "srm_wccl_17", "srm_wccl_20", "srm_wccl_25", "srm_wccl_32", "srm_wccl_37", "srm_wccl_41", "srm_wccl_45", "srm_wccl_46", "srm_wccl_52", "srm_wccl_55")))

# Items for BO
BO <- colnames(select(WCCL_Prep, c("srm_wccl_7", "srm_wccl_15", "srm_wccl_24", "srm_wccl_28", "srm_wccl_30", "srm_wccl_48")))

# Calculated Columns 
WCCL_Prep$wccl_SU_raw <- rowMeans(WCCL_Prep[,SU], na.rm = TRUE)

WCCL_Prep$wccl_GSC_raw <- rowMeans(WCCL_Prep[,GSC], na.rm = TRUE)

WCCL_Prep$wccl_BO_raw <- rowMeans(WCCL_Prep[,BO], na.rm = TRUE)

# Mean with 67% Rule#### 

# Check NA Percentage
WCCL_Prep$NACheck <- rowSums(is.na(select(WCCL_Prep, starts_with("srm"))))/ncol(dplyr::select(WCCL_Prep, starts_with("srm")))

# New Mean with 67% Rule 
WCCL_Prep$wccl_SU_cor <- ifelse(WCCL_Prep$NACheck < 0.67, rowMeans(WCCL_Prep[,SU], na.rm = TRUE), "NA")

WCCL_Prep$wccl_GSC_cor <- ifelse(WCCL_Prep$NACheck < 0.67, rowMeans(WCCL_Prep[,GSC], na.rm = TRUE), "NA")

WCCL_Prep$wccl_BO_cor <- ifelse(WCCL_Prep$NACheck < 0.67, rowMeans(WCCL_Prep[,BO], na.rm = TRUE), "NA")
```

```{r NDA Sheet}
# Create NDA structure column names
dbt_wccl <- paste("dbt_wccl", 1:59, sep = "")
NDA_Names <- c(dbt_wccl)

# Create NDA Prep structure 
NDA_WCCL_Prep <- select(WCCL_Prep, c(subjectkey = mom_guid, src_subject_id = mother_FamID, interview_date, interview_age, sex = mother_sex , visit = Timepoint, starts_with("srm")))
setnames(NDA_WCCL_Prep, new_WCCL_names, NDA_Names)

# bind NDA_WCCL_Prep and NDA structure  
NDA_WCCL <- bind_rows(NDA_WCCL, NDA_WCCL_Prep)

# recreate first row of NDA structure
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_WCCL))

NDA_WCCL <- bind_rows(NDA_WCCL, NDA_WCCL_Prep)
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_WCCL))

first_line[,1] <- "dbt_wccl"
first_line[,2] <- "1"
write.table(first_line, file = "dbt_wccl.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = TRUE, row.names = FALSE)
write.table(NDA_WCCL, file = "dbt_wccl.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = TRUE, row.names = FALSE)
```

```{r Table Preparation}
# Make Progress 
Progress <- select(WCCL_Prep, c(FamID, GroupAssignment, Timepoint, starts_with("srm"), NACheck))

# Change FamId as character and assign to ID variable 
ID <- c(as.character(Progress$FamID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")


# Drop people who are at less than 67% response
WCCL_DROP <- Progress[Progress$NACheck > 0.67, ]
WCCL_Prep67 <- Progress[Progress$NACheck <= 0.67, ]
WCCL_Prep100 <- Progress[Progress$NACheck == 0, ]

```

```{r Table 67%}

# Progress DBT_WCCL Table
Progress67 <- select(WCCL_Prep67, c(FamID, GroupAssignment, Timepoint, starts_with("srm")))

# Change FamId as character and assign to ID variable 
ID <- c(as.character(Progress67$FamID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress67$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# calculate rowmeans for each individual
Progress67$Row_Mean <- rowMeans(select(WCCL_Prep67,c(starts_with("srm"))), na.rm = T)

# Group by GroupAssignment and Timepoint, and calculate the Group Mean
Progress_Mean <- Progress67 %>%
  group_by(GroupAssignment,Timepoint,site) %>%
  summarise(GroupMean = mean(Row_Mean,na.rm = T),count = n())

# Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean 
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Calculate Both site Means 
Both_site_Mean <- Progress_Mean %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSiteMean = mean(GroupMean,na.rm = T),n = sum(count))

# Progress_Mean <- Progress_Mean[order(GroupAssignment),] 


# Change GroupMean Column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_WCCL"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_WCCL"

# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_WCCL")],UPMC[,"UPMC_WCCL"],Both_site_Mean[,c("BothSiteMean","n", "GroupAssignment")])

# Mean_Table <- select(Mean_Table, -c(GroupAssignment))

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name 
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Control Group means" = 4, "FSU means" = 4, "DBT Group means" = 4)) %>% add_header_above(c("WCCL Table Means 67%" = 13))%>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

```{r Table 100%}
# Progress DBT_WCCL Table
Progress100 <- select(WCCL_Prep100, c(FamID, GroupAssignment, Timepoint, starts_with("srm")))

# Change FamId as character and assign to ID variable 
ID <- c(as.character(Progress100$FamID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress100$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# Calculate rowmeans for each individual
Progress100$Row_Mean <- rowMeans(select(WCCL_Prep100,c(starts_with("srm"))), na.rm = T)

# Group by GroupAssignment and Timepoint, and calculate the Group Mean
Progress_Mean <- Progress100 %>%
  group_by(GroupAssignment,Timepoint,site) %>%
  summarise(GroupMean = mean(Row_Mean,na.rm = T),count = n())

# Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean 
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Calculate Both site Means 
Both_site_Mean <- Progress_Mean %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSiteMean = mean(GroupMean,na.rm = T),n = sum(count))

# Progress_Mean <- Progress_Mean[order(GroupAssignment),] 


# Change GroupMean Column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_WCCL"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_WCCL"

# Combine UO,UPMC and both_site data 
Mean_Table100 <- data.frame(UO[,c("UO_WCCL")],UPMC[,"UPMC_WCCL"],Both_site_Mean[,c("BothSiteMean","n", "GroupAssignment")])

# Mean_Table <- select(Mean_Table, -c(GroupAssignment))

# Convert Mean_Table, make original column as row
Mean_Table100 <- t(Mean_Table100)

# Make Mean_Table as a data.frame
Mean_Table100 <- data.frame(Mean_Table100)

Mean_Table100 <- Mean_Table100[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name 
setnames(Mean_Table100, names(Mean_Table100), Timepoint_names)

# Add a header 
kable(Mean_Table100) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Control Group means" = 4, "FSU means" = 4, "DBT Group means" = 4)) %>% add_header_above(c("WCCL Table Means 100%" = 13))%>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

```{r N's Table}
# Original Table ####
# Original by site
N_ori <- Progress %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_ori = n())

# Original both site 
N_ori_BothSite <- Progress %>%
  group_by(Timepoint, GroupAssignment) %>% 
  summarise(BothSite_Original_N = n())


# 67% table ####
# 67% by site 
N67 <- WCCL_Prep67 %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_67 = n())

# 67% both site 
N67_BothSite <- WCCL_Prep67 %>%
  group_by(Timepoint, GroupAssignment) %>% 
  summarise(BothSite_67_N = n())

# 100% table ####

# 100% by site
N100 <- WCCL_Prep100 %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_100 = n())

# 100% both site 
N100_BothSite <- WCCL_Prep100 %>%
  group_by(Timepoint, GroupAssignment) %>% 
  summarise(BothSite_100_N = n())

# N table ####

# combine all three n table 
N_bySite <- cbind(N_ori, N67, N100)
# Bind both site data 
BothSite_N <- cbind(N_ori_BothSite, N67_BothSite, N100_BothSite)


# Seperate UO and UPMC data 
UO_N <- data.frame(N_bySite[N_bySite$site == "UO",])
UPMC_N <- data.frame(N_bySite[N_bySite$site == "UPMC",])

# Change column names 
colnames(UO_N)[colnames(UO_N) == "n_ori"] = "UO_WCCL_Original_N"
colnames(UO_N)[colnames(UO_N) == "n_67"] = "UO_WCCL_67_N"
colnames(UO_N)[colnames(UO_N) == "n_100"] = "UO_WCCL_100_N"

colnames(UPMC_N)[colnames(UPMC_N) == "n_ori"] = "UPMC_WCCL_Original_N"
colnames(UPMC_N)[colnames(UPMC_N) == "n_67"] = "UPMC_WCCL_67_N"
colnames(UPMC_N)[colnames(UPMC_N) == "n_100"] = "UPMC_WCCL_100_N"

# Create N table (Selecting columns from UO_N, UPMC_N, BothSite_N)
N <- data.frame(UO_N[, c("Timepoint","UO_WCCL_Original_N", "UO_WCCL_67_N", "UO_WCCL_100_N")], 
                UPMC_N[, c("UPMC_WCCL_Original_N", "UPMC_WCCL_67_N", "UPMC_WCCL_100_N", "GroupAssignment")],
                BothSite_N[, c("BothSite_Original_N", "BothSite_67_N", "BothSite_100_N", "GroupAssignment")])

# Reorder N table base on GroupAssignment 
N <- N[order(N$GroupAssignment),]

# Convert data frame to numeric
N <- as.data.frame(sapply(N, as.numeric))

# Transfer N table from Horzontal to Vertical
N <- data.frame(t(N))

# Calculate Total N 
N$T1 <- rowSums(N[,c(1,5,9)])
N$T2 <- rowSums(N[,c(2,6,10)])
N$T3 <- rowSums(N[,c(3,7,11)])
N$T4 <- rowSums(N[,c(4,8,12)])

# Timepoint names 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4", "T1","T2", "T3", "T4")

# Rename column name 
setnames(N, names(N), Timepoint_names)

N <- N[-c(1,8,12),]


#Remove un-needed lines in table
#N <- N[-c(1,2,3),]

# Total number calculation 


kable(N) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  add_header_above(c(" " = 1, "DBT Group" = 4, "Control Group" = 4, "FSU Group" = 4, "Totals" = 4)) %>%
  add_header_above(c("Participant Numbers" = 17)) %>%
  column_spec(c(1,5,9,13), border_right = T, include_thead = T) %>%
  column_spec(2:17, width_min = "2cm", width_max = "2cm") %>%
  row_spec(7:9, background = "#d3d3d3")

```





