---
title: "Affect Perspective Taking"
author: "Jake Mulleavey"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
# Empty Global Environment
rm(list = ls())
```

## Import
Import Qualtrics excel files into R
```{r Import}
#Install Package, this only need to be done once.
#install.packages(c("dplyr","tidyverse","data.table","contrib.url","knitr"))
#install.packages('plyr', repos = "http://cran.us.r-project.org")

#Load packages, this need to be done every time you run this script. 
library(dplyr)
library(tidyverse)
library(data.table)
library(knitr)

#Set Working Directory
setwd("~/Documents/GitHub/DataUploadAutomation/Measures/PKBS/DataUploadAutomation/Measures/AffectPerspectiveTaking/")

#Import Pedigree and NDA Structure
Pedigree <- read.csv("Reference_Pedigree.csv")
NDA_AffectPT <- read.csv("apt01_template.csv", skip = 1)

#Import PKBS files from both sites and every timepoint
RedCap_Data <- read.csv("Redcap_Data.csv")
```

## Rename Columns and Create Prep Sheet
Select relevant data from master RedCap sheet. Recode child ratings to master code. Create Pedigree sheets, rename columns, add timepoint and combine with data to create Prep Sheet.
```{r Rename Columns and Create Prep Sheet}
#Select the relevant ID information and questions
AffectPT_Data <- select(RedCap_Data, fam_id, redcap_event_name, oc_apt_01, oc_apt_02, oc_apt_03, oc_apt_04, oc_apt_05, oc_apt_06, oc_apt_07, oc_apt_08)

#Convert each columns different child ratings into master recode
AffectPT_Data$oc_apt_01[which(AffectPT_Data$oc_apt_01 == "2")] = 1
AffectPT_Data$oc_apt_01[which(AffectPT_Data$oc_apt_01 == "4")] = 2
AffectPT_Data$oc_apt_01[which(AffectPT_Data$oc_apt_01 == "5")] = 3
AffectPT_Data$oc_apt_01[which(AffectPT_Data$oc_apt_01 == "6")] = 4

AffectPT_Data$oc_apt_02[which(AffectPT_Data$oc_apt_02 == "4")] = 1
AffectPT_Data$oc_apt_02[which(AffectPT_Data$oc_apt_02 == "2")] = 2
AffectPT_Data$oc_apt_02[which(AffectPT_Data$oc_apt_02 == "7")] = 3
AffectPT_Data$oc_apt_02[which(AffectPT_Data$oc_apt_02 == "8")] = 4

AffectPT_Data$oc_apt_03[which(AffectPT_Data$oc_apt_03 == "4")] = 1
AffectPT_Data$oc_apt_03[which(AffectPT_Data$oc_apt_03 == "7")] = 2
AffectPT_Data$oc_apt_03[which(AffectPT_Data$oc_apt_03 == "2")] = 3
AffectPT_Data$oc_apt_03[which(AffectPT_Data$oc_apt_03 == "8")] = 4

AffectPT_Data$oc_apt_04[which(AffectPT_Data$oc_apt_04 == "4")] = 1
AffectPT_Data$oc_apt_04[which(AffectPT_Data$oc_apt_04 == "7")] = 2
AffectPT_Data$oc_apt_04[which(AffectPT_Data$oc_apt_04 == "8")] = 3
AffectPT_Data$oc_apt_04[which(AffectPT_Data$oc_apt_04 == "2")] = 4

AffectPT_Data$oc_apt_05[which(AffectPT_Data$oc_apt_05 == "2")] = 1
AffectPT_Data$oc_apt_05[which(AffectPT_Data$oc_apt_05 == "4")] = 2
AffectPT_Data$oc_apt_05[which(AffectPT_Data$oc_apt_05 == "5")] = 3
AffectPT_Data$oc_apt_05[which(AffectPT_Data$oc_apt_05 == "6")] = 4

AffectPT_Data$oc_apt_06[which(AffectPT_Data$oc_apt_06 == "4")] = 1
AffectPT_Data$oc_apt_06[which(AffectPT_Data$oc_apt_06 == "2")] = 2
AffectPT_Data$oc_apt_06[which(AffectPT_Data$oc_apt_06 == "7")] = 3
AffectPT_Data$oc_apt_06[which(AffectPT_Data$oc_apt_06 == "8")] = 4

AffectPT_Data$oc_apt_07[which(AffectPT_Data$oc_apt_07 == "4")] = 1
AffectPT_Data$oc_apt_07[which(AffectPT_Data$oc_apt_07 == "7")] = 2
AffectPT_Data$oc_apt_07[which(AffectPT_Data$oc_apt_07 == "8")] = 3
AffectPT_Data$oc_apt_07[which(AffectPT_Data$oc_apt_07 == "2")] = 4

AffectPT_Data$oc_apt_08[which(AffectPT_Data$oc_apt_08 == "4")] = 1
AffectPT_Data$oc_apt_08[which(AffectPT_Data$oc_apt_08 == "7")] = 2
AffectPT_Data$oc_apt_08[which(AffectPT_Data$oc_apt_08 == "2")] = 3
AffectPT_Data$oc_apt_08[which(AffectPT_Data$oc_apt_08 == "8")] = 4

#Convert timepoint string input into 1 through 4 numerical value
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_1_arm_1")] = 1
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_1_arm_2")] = 1
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_2_arm_1")] = 2
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_2_arm_2")] = 2
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_3_arm_1")] = 3
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_3_arm_2")] = 3
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_4_arm_1")] = 4
AffectPT_Data$redcap_event_name[which(AffectPT_Data$redcap_event_name == "time_4_arm_2")] = 4

#Rename timepoint and Fam ID columns
names(AffectPT_Data)[names(AffectPT_Data) == "redcap_event_name"] <- "timepoint"
names(AffectPT_Data)[names(AffectPT_Data) == "fam_id"] <- "Fam_ID"

#Create Pedigree sheets for each timepoint
Pedigree_T1 <- select(Pedigree, FamID, child_guid, FamID_Child, Time1Date, ChildAge_T1, ChildGender, GroupAssignment)
Pedigree_T2 <- select(Pedigree, FamID, child_guid, FamID_Child, Time2Date, ChildAge_T2, ChildGender, GroupAssignment)
Pedigree_T3 <- select(Pedigree, FamID, child_guid, FamID_Child, Time3Date, ChildAge_T3, ChildGender, GroupAssignment)
Pedigree_T4 <- select(Pedigree, FamID, child_guid, FamID_Child, Time4Date, ChildAge_T4, ChildGender, GroupAssignment)

#Rename Age and Interview Date columns for each timepoint
names(Pedigree_T1)[names(Pedigree_T1) == "ChildAge_T1"] <- "interview_age"
names(Pedigree_T1)[names(Pedigree_T1) == "Time1Date"] <- "interview_date"
names(Pedigree_T2)[names(Pedigree_T2) == "ChildAge_T2"] <- "interview_age"
names(Pedigree_T2)[names(Pedigree_T2) == "Time2Date"] <- "interview_date"
names(Pedigree_T3)[names(Pedigree_T3) == "ChildAge_T3"] <- "interview_age"
names(Pedigree_T3)[names(Pedigree_T3) == "Time3Date"] <- "interview_date"
names(Pedigree_T4)[names(Pedigree_T4) == "ChildAge_T4"] <- "interview_age"
names(Pedigree_T4)[names(Pedigree_T4) == "Time4Date"] <- "interview_date"

#Add timepoint
Pedigree_T1$timepoint=1
Pedigree_T2$timepoint=2
Pedigree_T3$timepoint=3
Pedigree_T4$timepoint=4

#Combine each Pedigree timepoint dataframe into a single one
Pedigree_Prep <- rbind(Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)
names(Pedigree_Prep)[names(Pedigree_Prep) == "FamID"] <- "Fam_ID"

#Combine the Pedigree information with the RedCap data to output the Prep Sheet
AffectPT_Prep <- merge(Pedigree_Prep, AffectPT_Data, by = c("timepoint", "Fam_ID"), all = TRUE)

#Convert column names to odd numbers to represent participant response
old_AffectPT_names <- c("oc_apt_01", "oc_apt_02", "oc_apt_03", "oc_apt_04", "oc_apt_05", "oc_apt_06", 
                        "oc_apt_07", "oc_apt_08")
new_AffectPT_names <- c("oc_apt_01", "oc_apt_03", "oc_apt_05", "oc_apt_07", "oc_apt_09", "oc_apt_11", 
                        "oc_apt_13", "oc_apt_15")
setnames(AffectPT_Prep, old_AffectPT_names, new_AffectPT_names, skip_absent = FALSE)

#Clean Global Environment
rm(AffectPT_Data, Pedigree_Prep, Pedigree, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)
```

## Add Scoring and Calculated Columns
For the Affect Perspective Taking task there are two scores; the child's rating and whether or not they answer the task correctly, incorrectly or was within the correct valence. The scores in the previous prep sheet is the child's rating so now we have to add the scoring columns. After, create a sums column for the added scores.
```{r Calculated Columns}
#Add empty scoring column to the existing data frame
AffectPT_Prep[, c("oc_apt_02", "oc_apt_04", "oc_apt_06", "oc_apt_08", "oc_apt_10", "oc_apt_12", 
                  "oc_apt_14", "oc_apt_16")] <- NA

#Reorder scoring columns with existing child response columns
col_order <- c("timepoint", "Fam_ID", "child_guid", "FamID_Child", "interview_date", "interview_age", 
               "ChildGender", "GroupAssignment", "oc_apt_01", "oc_apt_02", "oc_apt_03", "oc_apt_04", 
               "oc_apt_05", "oc_apt_06", "oc_apt_07", "oc_apt_08", "oc_apt_09", "oc_apt_10", "oc_apt_11", 
               "oc_apt_12", "oc_apt_13", "oc_apt_14", "oc_apt_15", "oc_apt_16")

AffectPT_Prep <- AffectPT_Prep[, col_order]

#Add values dependant on previous child's rating column into each scoring column
AffectPT_Prep$oc_apt_02 <- ifelse(AffectPT_Prep$oc_apt_01 == 1, 2, 0)

AffectPT_Prep$oc_apt_04 <- ifelse(AffectPT_Prep$oc_apt_03 == 2, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_03 == 3, 1,
                                         ifelse(AffectPT_Prep$oc_apt_03 == 4, 1, 0)))

AffectPT_Prep$oc_apt_06 <- ifelse(AffectPT_Prep$oc_apt_05 == 3, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_05 == 2, 1,
                                         ifelse(AffectPT_Prep$oc_apt_05 == 4, 1, 0)))

AffectPT_Prep$oc_apt_08 <- ifelse(AffectPT_Prep$oc_apt_07 == 4, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_07 == 2, 1,
                                         ifelse(AffectPT_Prep$oc_apt_07 == 3, 1, 0)))

AffectPT_Prep$oc_apt_10 <- ifelse(AffectPT_Prep$oc_apt_09 == 1, 2, 0)

AffectPT_Prep$oc_apt_12 <- ifelse(AffectPT_Prep$oc_apt_11 == 2, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_11 == 3, 1,
                                         ifelse(AffectPT_Prep$oc_apt_11 == 4, 1, 0)))

AffectPT_Prep$oc_apt_14 <- ifelse(AffectPT_Prep$oc_apt_13 == 4, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_13 == 2, 1,
                                         ifelse(AffectPT_Prep$oc_apt_13 == 3, 1, 0)))

AffectPT_Prep$oc_apt_16 <- ifelse(AffectPT_Prep$oc_apt_15 == 3, 2, 
                                  ifelse(AffectPT_Prep$oc_apt_15 == 2, 1,
                                         ifelse(AffectPT_Prep$oc_apt_15 == 4, 1, 0)))

#Add aggregate total column for all the scoring columns
AffectPT_Prep <- add_column(AffectPT_Prep, oc_apt_total = rowSums(AffectPT_Prep[, c("oc_apt_02", "oc_apt_04", "oc_apt_06", "oc_apt_08", "oc_apt_10", "oc_apt_12", "oc_apt_14", "oc_apt_16")]))
```

##Implement 67% Rule
Add a NA Check that calculates the decimal of what percentage of the data is present for a Fam ID.
```{r Implement 67% Rule}
#Create NA Check column (1.00 means 100% of the data is present)
AffectPT_Prep$NACheck <- rowSums(is.na(select(AffectPT_Prep, starts_with("oc_apt_"))))/ncol(dplyr::select(AffectPT_Prep, starts_with("oc_apt_")))

#Create Drop sheet where ID's that have less than 67% of data go; Rest of the ID's remain in Prep Sheet
AffectPT_Drop <- AffectPT_Prep[AffectPT_Prep$NACheck > 0.67, ]
AffectPT_Prep <- AffectPT_Prep[AffectPT_Prep$NACheck <= 0.67, ]

#Create 100% Sheet that only contains ID's with 100% of data
AffectPT_100 <- AffectPT_Prep[AffectPT_Prep$NACheck == 0, ]
```

## NDA Structure
Re-name Affect Perspective Taking Prep Sheet columns to match NDA specifications. 
```{r NDA Structure}
#Select relevant columns from Prep Sheet to move into NDA Prep template
NDA_AffectPT_Prep <- select(AffectPT_Prep, c(subjectkey = child_guid, src_subject_id = FamID_Child, interview_date, interview_age, sex = ChildGender, visit = timepoint, starts_with("oc_apt")))

#Match Prep Sheet column names to required NDA names
nda_names <- c(paste("apt", 1:16, sep = ""))
prep_names <- c("oc_apt_01", "oc_apt_02", "oc_apt_03", "oc_apt_04", 
               "oc_apt_05", "oc_apt_06", "oc_apt_07", "oc_apt_08", "oc_apt_09", "oc_apt_10", "oc_apt_11", 
               "oc_apt_12", "oc_apt_13", "oc_apt_14", "oc_apt_15", "oc_apt_16")
setnames(NDA_AffectPT_Prep, prep_names, nda_names, skip_absent = FALSE)

#Drop total column
NDA_AffectPT <- NDA_AffectPT[-c(23)]

#Combine NDA Template with NDA Structure
NDA_AffectPT[1,] <- NA
NDA_AffectPT <- bind_rows(NDA_AffectPT, NDA_AffectPT_Prep)

first_line <- matrix("", nrow = 1, ncol = ncol(NDA_AffectPT))
first_line[,1] <- "apt"
first_line[,2] <- "1"
```

## Table
Create descriptives means table.
```{r Table}
library(knitr)
library(magrittr)
library(kableExtra)

#Select necessary columns for means table
Progress <- select((AffectPT_Prep), c(Fam_ID, GroupAssignment, timepoint, starts_with("oc")))

#Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$Fam_ID))

#Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

#Group by GroupAssignment and Timepoint, and calculate Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(GroupMean = mean(oc_apt_total, na.rm = T), count = n())

#Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
#Select only UPMC Mean
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

#Calculate mean from both sites
Both_Site_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise(BothSiteMean = mean(oc_apt_total, na.rm = T), n = sum(count = n()))

#Change GroupMean column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_APT"
colnames(UO)[colnames(UO) == "count"] = "UO_APT_Original_N"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_APT"
colnames(UPMC)[colnames(UPMC) == "count"] = "UPMC_APT_Original_N"
colnames(Both_Site_Mean)[colnames(Both_Site_Mean) == "n"] = "BothSite_Original_N"

#Combine UO, UPMC, Both_Site, Bear and Dragon data 
Mean_Table <- data.frame(UO[,c("UO_APT","GroupAssignment")],UPMC[,c("UPMC_APT")],Both_Site_Mean[,c("BothSiteMean","BothSite_Original_N")])

#Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

#Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

#Re-order Mean Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

#Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

#Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

#Create Table
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("Affect Perspective Taking Table Means" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

## 100% Table
Descriptive means table for ID's with 100% of their data.
```{r 100% Table}
#Select necessary columns for means table
Progress100 <- select((AffectPT_100), c(Fam_ID, GroupAssignment, timepoint, starts_with("oc")))

#Change FamID as character and assign to ID variable
ID <- c(as.character(Progress100$Fam_ID))

#Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress100$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

#Group by GroupAssignment and Timepoint, and calculate Group Mean
Progress100_Mean <- Progress100 %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(GroupMean = mean(oc_apt_total, na.rm = T), count = n())

#Select only UO Mean
UO100 <- Progress100_Mean[Progress100_Mean$site == "UO",]
#Select only UPMC Mean
UPMC100 <- Progress100_Mean[Progress100_Mean$site == "UPMC",]

#Calculate mean from both sites
Both_Site_Mean100 <- Progress100 %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise(BothSiteMean = mean(oc_apt_total, na.rm = T), n = sum(count = n()))

#Change GroupMean column names according to site
colnames(UO100)[colnames(UO100) == "GroupMean"] = "UO100_APT"
colnames(UO100)[colnames(UO100) == "count"] = "UO100_APT_N"
colnames(UPMC100)[colnames(UPMC100) == "GroupMean"] = "UPMC100_APT"
colnames(UPMC100)[colnames(UPMC100) == "count"] = "UPMC100_APT_N"
colnames(Both_Site_Mean100)[colnames(Both_Site_Mean100) == "n"] = "BothSite100_N"

#Combine UO, UPMC, Both_Site, Bear and Dragon data 
Mean_Table100 <- data.frame(UO100[,c("UO100_APT","GroupAssignment")],UPMC100[,c("UPMC100_APT")],
                            Both_Site_Mean100[,c("BothSiteMean","BothSite100_N")])

#Convert Mean_Table, make original column as row
Mean_Table100 <- t(Mean_Table100)

#Make Mean_Table a data frame
Mean_Table100 <- data.frame(Mean_Table)

#Re-order Mean Table
Mean_Table100 <- Mean_Table100[c(5,6,7,8,9,10,11,12,1,2,3,4)]

#Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

#Rename column name
setnames(Mean_Table100, names(Mean_Table100), Timepoint_names)

#Create Table
kable(Mean_Table100) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("Affect Perspective Taking Table Means (100%)" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

## N Table
Create table for participant numbers.
```{r N Table}
#Create N table, GroupAssignment and Timepoint are dupliced here, just checking it's align
N <- data.frame(UO[, c("timepoint", "UO_APT_Original_N", "GroupAssignment")],
                UO100[, c("timepoint", "UO100_APT_N", "GroupAssignment")],
                UPMC[, c("timepoint", "UPMC_APT_Original_N", "GroupAssignment")],
                UPMC100[, c("timepoint", "UPMC100_APT_N", "GroupAssignment")],
                Both_Site_Mean[,c("timepoint", "BothSite_Original_N", "GroupAssignment")],
                Both_Site_Mean100[,c("timepoint", "BothSite100_N", "GroupAssignment")]
                )
#Remove dupliced column 
N <- N[,-c(1,3,4,6,7,9,10,12,13,15,16,18,19,21,22,24,25,27)]


#Convert data frame to numeric
N <- as.data.frame(sapply(N, as.numeric))

#Transfer N table from Horzontal to Vertical
N <- data.frame(t(N))

#Calculate Total N 
N$T1 <- rowSums(N[,c(1,5,9)])
N$T2 <- rowSums(N[,c(2,6,10)])
N$T3 <- rowSums(N[,c(3,7,11)])
N$T4 <- rowSums(N[,c(4,8,12)])

#Timepoint names 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4", "T1","T2", "T3", "T4")

#Rename column name 
setnames(N, names(N), Timepoint_names)

#Create Table
kable(N) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  add_header_above(c(" " = 1, "DBT Group" = 4, "Control Group" = 4, "FSU Group" = 4, "Totals" = 4)) %>%
  add_header_above(c("Participant Numbers" = 17)) %>%
  column_spec(c(1,5,9,13), border_right = T, include_thead = T) %>%
  column_spec(1:16, width_min = "2cm", width_max = "5cm") %>%
  row_spec(1:6, background = "#d3d3d3")
```

