---
title: "AutomatingtheDataUpload - DimensionalCardSort"
author: "Min Zhang"
date: "6/1/2020"
output: html_document
---
# Setup
Empty environment, loading library, set knitr and scientific notation
```{r setup}
#install.packages("flextable")
# Load package
library(tidyverse)
library(dplyr)
library(data.table)
library(knitr)
library(kableExtra)

# Knit set up
# Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
knitr::opts_chunk$set(echo = TRUE, include = FALSE)

#scientific notation, round up to 3 digits
options(digits = 3)
```

# Import
Import measurement, Pedigree data and NDA structure
```{r Import}
# Empty Global Environment
rm(list = ls())

# Importe needed fils 
Pedigree <- read.csv("Reference_Pedigree.csv", stringsAsFactors = FALSE)
Redcap_Data <- read.csv("Redcap_Data.csv", stringsAsFactors = FALSE)

NDA_DCCS <- read.csv("dccs01_template.csv", skip = 1, stringsAsFactors = FALSE)
```

# Rename Columns
Create old & new variable names
Old DCS name: oc_dcs_01 ~ oc_dcs_36
NDA name: dcs01 ~ dcs36
```{r Rename Columns}
# Redcap column name: oc_dcs_1:36
old_DCS_names <- sprintf("oc_dcs_%02d", 1:36)

# DCCS NDA Columns Name TODO:wait for Bryan to confirm
NDA_DCS_names <- sprintf("dcs%02d", 1:36)
```
#Prep Sheet
Select relevant pedigree information, rename as needed. (Include GroupAssignment for treatment progress calculation.)
```{r Prep Sheet}
# Assign Timepoint base on redcap_event_name
Redcap_Data$Timepoint = sapply(strsplit(as.character(Redcap_Data$redcap_event_name), split = '_', fixed = T), function(x) (x[2])) 

# Select needed columns and rename in Redcap_Data
Redcap_Data <- select(Redcap_Data, c(Fam_ID = fam_id,  Timepoint, starts_with("oc_dcs_")))
Redcap_Data <- select(Redcap_Data, -c(oc_dcs_notes))

# Select revelent pedigree information, rename as needed. (Include GroupAssignment for treatment progross calculation.)
Pedigree_T1 <- data.frame(select(Pedigree, Fam_ID =  FamID, child_guid, child_famID = FamID_Child, interview_date = Time1Date, interview_age = MomAge_T1, child_sex = ChildGender, GroupAssignment), Timepoint = 1 )
Pedigree_T2 <- data.frame(select(Pedigree, Fam_ID =  FamID, child_guid, child_famID = FamID_Child, interview_date = Time2Date, interview_age = MomAge_T2, child_sex = ChildGender, GroupAssignment), Timepoint = 2 )
Pedigree_T3 <- data.frame(select(Pedigree, Fam_ID =  FamID, child_guid, child_famID = FamID_Child, interview_date = Time3Date, interview_age = MomAge_T3, child_sex = ChildGender, GroupAssignment), Timepoint = 3 )
Pedigree_T4 <- data.frame(select(Pedigree, Fam_ID =  FamID, child_guid, child_famID = FamID_Child, interview_date = Time4Date, interview_age = MomAge_T4, child_sex = ChildGender, GroupAssignment), Timepoint = 4 )

# Merge 4 pedigree
Pedigree_Prep <- rbind(Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)

# Merge Pedigree and redcap files
DCS_Prep <- merge(Pedigree_Prep, Redcap_Data,by = c("Timepoint","Fam_ID"), all = TRUE)

# Clean Environment
rm(Pedigree, Pedigree_Prep, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4, Redcap_Data)
```

# Recode
```{r Re-code}
# Re=-code UO Groupassignment 
DCS_Prep <- DCS_Prep %>% 
  mutate_at(c("GroupAssignment"),
            funs(recode(., "Assigned Group 3 (HC)" = "Healthy", 
                        'Assigned Group 2 (FSU)' = "NO DBT",
                        'Assigned Group 1 (DBT)' = "DBT")))
```

```{r Colculated Columns}
# TODO: apply 67% rule 
# Check NA percentage   0:100%data     1 0% data 
DCS_Prep$NACheck <- rowSums(is.na(select(DCS_Prep, starts_with("srm"))))/ncol(dplyr::select(DCS_Prep, starts_with("srm")))
```

#NDA Sheet
```{r NDA Sheet}
# Create NDA Prep sheet, select all the needed columns from Prep sheet
NDA_DCCS_Prep <- select(DCS_Prep, c(subjectkey = child_guid, src_subject_id = child_famID, interview_date, interview_age, sex = child_sex, visit = Timepoint, starts_with("oc_dcs_") ))

# Replace columns name 
setnames(NDA_DCCS_Prep, old_DCS_names, NDA_DCS_names)

# Add empty line in original NDA file for merge
NDA_DCCS[1,] <- NA
# Recreate first line in original NDA file
NDA_DCCS <- bind_rows(NDA_DCCS, NDA_DCCS_Prep)
first_line <- matrix("", nrow = 1, ncol = ncol(NDA_DCCS))
first_line[,1] <- "dccs"
# assign the second cell in first_line as dccs
first_line[,2] <- "1"

# NDA output ####
# Create a new file in folder called dccs.csv, and put first line into this file
# dccs.csv file will be saved into same folder as current r script
write.table(first_line, file = "dccs01.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = FALSE, row.names = FALSE)

# Append data in NDA_DCCS into dccs.csv file 
write.table(NDA_DCCS, file = 'dccs01.csv', sep = ",", append = TRUE, na = "", quote = FALSE, row.names = FALSE)
```


# All responsees Table 
Mean Table with all data (no drop)
```{r All responsees Table}
# Treatment Progress sheet
# Select needed column
Progress <- select(DCS_Prep, c(Fam_ID, GroupAssignment, Timepoint, starts_with("oc_dcs_"), NACheck))

# Calculate row mean for each individual  ss
Progress$Row_Mean <- rowMeans(select(DCS_Prep,c(starts_with("oc_dcs_"))), na.rm = T)

# Change FamId as character and assign to ID variable 
ID <- c(as.character(Progress$Fam_ID))

# Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"),"UO","UPMC")

# Group by GroupAssissignment and Timepoint, and calculate the Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment,Timepoint,site) %>%
  summarise(GroupMean = mean(Row_Mean, na.rm = T),count = n())

# Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean 
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Colculate Both site Mean 
Both_site_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSite_DimensionalCardSort_Mean = mean(Row_Mean,na.rm = T),n = n())
#Progress_Mean <- Progress_Mean[order(GroupAssignment),] 


# Change GroupMean Column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_DimensionalCardSort"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_DimensionalCardSort"

# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_DimensionalCardSort")],UPMC[,"UPMC_DimensionalCardSort"],Both_site_Mean[,c("BothSite_DimensionalCardSort_Mean","n","GroupAssignment")])

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

# Reorder Mean_Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name 
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Table output ####
# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "DBT Group means" = 4, "Controls Group means" = 4, "FSU Group means" = 4)) %>%
  add_header_above(c("Dimensional Card Sort Mean Table" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

# 67% Responses Table
Drop participant have less than 67% data 
```{r 67% Responses Table}
# Drop participant who has less than 67% data
DCS_DROP <- Progress[Progress$NACheck > 0.67, ]
# Data contain 67% data or more
Progress67 <- Progress[Progress$NACheck <= 0.67, ]

# Group by GroupAssissignment and Timepoint, and calculate the Group Mean
Progress_Mean67 <- Progress67 %>%
  group_by(GroupAssignment,Timepoint,site) %>%
  summarise(GroupMean67 = mean(Row_Mean, na.rm = T),count = n())

# Select only UO Mean
UO67 <- Progress_Mean67[Progress_Mean67$site == "UO",]
# Select only UPMC Mean 
UPMC67 <- Progress_Mean67[Progress_Mean67$site == "UPMC",]

# Colculate Both site Mean 
Both_site_Mean67 <- Progress67 %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSite_DimensionalCardSort_Mean67 = mean(Row_Mean,na.rm = T),n = n())
#Progress_Mean <- Progress_Mean[order(GroupAssignment),] 


# Change GroupMean Column names according to site
colnames(UO67)[colnames(UO67) == "GroupMean67"] = "UO_DimensionalCardSort"
colnames(UPMC67)[colnames(UPMC67) == "GroupMean67"] = "UPMC_DimensionalCardSort"

# Combine UO,UPMC and both_site data 
Mean_Table67 <- data.frame(UO67[,c("UO_DimensionalCardSort")],UPMC67[,"UPMC_DimensionalCardSort"],Both_site_Mean67[,c("BothSite_DimensionalCardSort_Mean67","n","GroupAssignment")])

# Convert Mean_Table, make original column as row
Mean_Table67 <- t(Mean_Table67)

# Make Mean_Table as a data.frame
Mean_Table67 <- data.frame(Mean_Table67)

# Reorder Mean_Table
Mean_Table67 <- Mean_Table67[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name 
setnames(Mean_Table67, names(Mean_Tabl67e), Timepoint_names)

# Table output ####
# Add a header 
kable(Mean_Table67) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "DBT Group means" = 4, "Controls Group means" = 4, "FSU Group means" = 4)) %>%
  add_header_above(c("Dimensional Card Sort Mean Table" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

# 100% Responses Table
Drop participant have less than 100% data 
```{r 100% Responses Table}
# Data contain 100% data
Progress100 <- Progress[Progress$NACheck == 0, ]

# Group by GroupAssissignment and Timepoint, and calculate the Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment,Timepoint,site) %>%
  summarise(GroupMean = mean(Row_Mean, na.rm = T),count = n())

# Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
# Select only UPMC Mean 
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

# Colculate Both site Mean 
Both_site_Mean <- Progress %>%
  group_by(GroupAssignment, Timepoint) %>%
  summarise(BothSite_DimensionalCardSort_Mean = mean(Row_Mean,na.rm = T),n = n())
#Progress_Mean <- Progress_Mean[order(GroupAssignment),] 


# Change GroupMean Column names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_DimensionalCardSort"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_DimensionalCardSort"

# Combine UO,UPMC and both_site data 
Mean_Table <- data.frame(UO[,c("UO_DimensionalCardSort")],UPMC[,"UPMC_DimensionalCardSort"],Both_site_Mean[,c("BothSite_DimensionalCardSort_Mean","n","GroupAssignment")])

# Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

# Make Mean_Table as a data.frame
Mean_Table <- data.frame(Mean_Table)

# Reorder Mean_Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

# Add Timepoint column 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

# Rename column name 
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

# Table output ####
# Add a header 
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "DBT Group means" = 4, "Controls Group means" = 4, "FSU Group means" = 4)) %>%
  add_header_above(c("Dimensional Card Sort Mean Table" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = T) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

# Ns Table
```{r Ns Table}
# Orig
N_org <- Progress %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_orig = n())


# 67%
N67 <- Progress67 %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_67 = n())

# 100%
N100 <- Progress100 %>%
  group_by(Timepoint, site, GroupAssignment) %>% 
  summarise(n_100 = n())

N <- cbind(N_org, N67, N100)
N <- N[,-c(5,6,7,9, 10, 11)]
N <- data.frame(t(N))

kable(N) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  add_header_above(c(" " = 1, "DBT Group" = 4, "Control Group" = 4, "FSU Group" = 4, "Totals" = 4)) %>%
  add_header_above(c("Participant Numbers" = 17)) %>%
  column_spec(c(1,5,9,13), border_right = T, include_thead = T) %>%
  column_spec(2:17, width_min = "2cm", width_max = "2cm") %>%
  row_spec(7:9, background = "#d3d3d3")
  
```
