---
title: "BearDragon"
author: "Jake Mulleavey"
date: "7/16/2020"
output: html_document
---

```{r Setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

## Import
Import Qualtrics Excel files into R
```{r}
# Empty Global Enivronment
rm(list = ls())

#Install Package, this only need to be done once.
#install.packages(c("dplyr","tidyverse","data.table","knitr"))
#install.packages('plyr', repos = "http://cran.us.r-project.org")

#Load packages, this need to be done every time you run this script. 
library(dplyr)
library(tidyverse)
library(data.table)
library(knitr)

#Set Working Directory
setwd("~/Documents/GitHub/DataUploadAutomation/DataUploadAutomation/Measures/BearDragon/")

#Import Pedigree and NDA Structure
Pedigree <- read.csv("Reference_Pedigree.csv")
NDA_BearDragon <- read.csv("beardragon01_template.csv")

#Import Bear Dragon REDCap Data
BearDragon_Data <- read.csv("Redcap_Data.csv", stringsAsFactors = FALSE)
```

## Rename Columns and Create Prep Sheet
Rename questions numbers to self-report measure scale items. Then, take each scale measure from both sites and combine them by timepoint. Finally, combine Pedigree information with RedCap data to get the Prep Sheet.
```{r Rename Columns and Prep Sheet}
#Select the relevant ID information and questions
RedCap_Data <- select(BearDragon_Data, fam_id, redcap_event_name, oc_bd_01, oc_bd_02, oc_bd_03, oc_bd_04,
                      oc_bd_05, oc_bd_06, oc_bd_07, oc_bd_08, oc_bd_09, oc_bd_10)

#Convert timepoint string input into 1 through 4 numerical value
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_1_arm_1")] = 1
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_1_arm_2")] = 1
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_2_arm_1")] = 2
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_2_arm_2")] = 2
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_3_arm_1")] = 3
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_3_arm_2")] = 3
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_4_arm_1")] = 4
RedCap_Data$redcap_event_name[which(RedCap_Data$redcap_event_name == "time_4_arm_2")] = 4

#Rename timepoint and Fam ID columns
names(RedCap_Data)[names(RedCap_Data) == "redcap_event_name"] <- "timepoint"
names(RedCap_Data)[names(RedCap_Data) == "fam_id"] <- "Fam_ID"

#Create Pedigree sheets for each timepoint
Pedigree_T1 <- select(Pedigree, FamID, child_guid, FamID_Child, Time1Date, ChildAge_T1, ChildGender, GroupAssignment)
Pedigree_T2 <- select(Pedigree, FamID, child_guid, FamID_Child, Time2Date, ChildAge_T2, ChildGender, GroupAssignment)
Pedigree_T3 <- select(Pedigree, FamID, child_guid, FamID_Child, Time3Date, ChildAge_T3, ChildGender, GroupAssignment)
Pedigree_T4 <- select(Pedigree, FamID, child_guid, FamID_Child, Time4Date, ChildAge_T4, ChildGender, GroupAssignment)

#Rename Age and Interview Date columns for each timepoint
names(Pedigree_T1)[names(Pedigree_T1) == "ChildAge_T1"] <- "interview_age"
names(Pedigree_T1)[names(Pedigree_T1) == "Time1Date"] <- "interview_date"
names(Pedigree_T2)[names(Pedigree_T2) == "ChildAge_T2"] <- "interview_age"
names(Pedigree_T2)[names(Pedigree_T2) == "Time2Date"] <- "interview_date"
names(Pedigree_T3)[names(Pedigree_T3) == "ChildAge_T3"] <- "interview_age"
names(Pedigree_T3)[names(Pedigree_T3) == "Time3Date"] <- "interview_date"
names(Pedigree_T4)[names(Pedigree_T4) == "ChildAge_T4"] <- "interview_age"
names(Pedigree_T4)[names(Pedigree_T4) == "Time4Date"] <- "interview_date"

#Add timepoint
Pedigree_T1$timepoint=1
Pedigree_T2$timepoint=2
Pedigree_T3$timepoint=3
Pedigree_T4$timepoint=4

#Combine each Pedigree timepoint dataframe into a single one
Pedigree_Prep <- rbind(Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)
names(Pedigree_Prep)[names(Pedigree_Prep) == "FamID"] <- "Fam_ID"

#Combine the Pedigree information with the RedCap data to output the Prep Sheet
BearDragon_Prep <- merge(Pedigree_Prep, RedCap_Data, by = c("timepoint", "Fam_ID"), all = TRUE)

#Clean Global Environment
rm(BearDragon_Data, Pedigree_Prep, Pedigree, Pedigree_T1, Pedigree_T2, Pedigree_T3, Pedigree_T4)
```

## Calculated Columns
Create sums column combining each individual measure. 
```{r Calculated Columns}
#Add total column for all data
BearDragon_Prep <- add_column(BearDragon_Prep, oc_beardragon_total = rowSums(BearDragon_Prep[, c("oc_bd_01", "oc_bd_02", "oc_bd_03", "oc_bd_04", "oc_bd_05", "oc_bd_06", "oc_bd_07", "oc_bd_08", "oc_bd_09", "oc_bd_10")]))

#Add total column for bear data
BearDragon_Prep <- add_column(BearDragon_Prep, oc_bear_total = rowSums(BearDragon_Prep[, c("oc_bd_01", "oc_bd_03", "oc_bd_05", "oc_bd_07", "oc_bd_09")]))

#Add total column for dragon data
BearDragon_Prep <- add_column(BearDragon_Prep, oc_dragon_total = rowSums(BearDragon_Prep[, c("oc_bd_02", "oc_bd_04", "oc_bd_06", "oc_bd_08", "oc_bd_10")]))
```

##Implement 67% Rule
Add a NA Check that calculates the decimal of what percentage of the data is present for a Fam ID.
```{r Implement 67% Rule}
#Create NA Check column (1.00 means 100% of the data is present)
BearDragon_Prep$NACheck <- rowSums(is.na(select(BearDragon_Prep, starts_with("oc_bd_"))))/ncol(dplyr::select(BearDragon_Prep, starts_with("oc_bd_")))

#Create Drop sheet where ID's that have less than 67% of data go; Rest of the ID's remain in Prep Sheet
BearDragon_Drop <- BearDragon_Prep[BearDragon_Prep$NACheck > 0.67, ]
BearDragon_Prep <- BearDragon_Prep[BearDragon_Prep$NACheck <= 0.67, ]

#Create 100% Sheet that only contains ID's with 100% of data
BearDragon_100 <- BearDragon_Prep[BearDragon_Prep$NACheck == 0, ]
```

## NDA Structure
Re-name Bear Dragon Prep Sheet columns to match NDA specifications. 
```{r NDA Structure}
#Select relevant columns from Prep Sheet to move into NDA Prep template
NDA_BearDragon_Prep <- select(BearDragon_Prep, c(subjectkey = child_guid, src_subject_id = FamID_Child, interview_date, interview_age, sex = ChildGender, visit = timepoint, starts_with("oc_bd")))

#Match Prep Sheet column names to required NDA names
nda_names <- c(paste("beardragon", 1:10, sep = ""))
prep_names <- c(paste("oc_bd_", 01:10, sep = "0"))
setnames(NDA_BearDragon_Prep, prep_names, nda_names, skip_absent = TRUE)

#Combine NDA Template with NDA Structure
NDA_BearDragon[1,] <- NA
NDA_BearDragon <- bind_rows(NDA_BearDragon, NDA_BearDragon_Prep)

first_line <- matrix("", nrow = 1, ncol = ncol(NDA_BearDragon))
first_line[,1] <- "beardragon"
first_line[,2] <- "1"

# Create a new file in folder called pabq.csv, and put first line into this file
# pabq.csv file will be saved into same folder as current r script
write.table(first_line, file = "beardragon.csv", sep = ",", append = FALSE, quote = FALSE, na = "", col.names = FALSE, row.names = FALSE)

# Append data in NDA_CCNES into pabq.cav file 
write.table(NDA_BearDragon, file = 'beardragon.csv', sep = ",", append = TRUE, na = "", quote = FALSE, row.names = FALSE)
```

## Table
Create descriptive means table.
```{r Table}
library(knitr)
library(magrittr)
library(kableExtra)

#Select necessary columns for means table
Progress <- select((BearDragon_Prep), c(Fam_ID, GroupAssignment, timepoint, starts_with("oc")))
Progress$Row_Mean <- rowMeans(select(BearDragon_Prep, starts_with("oc_bd_")), na.rm = T)

#Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$Fam_ID))

#Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

#Group by GroupAssignment and Timepoint, and calculate Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(GroupMean = mean(oc_beardragon_total, na.rm = T), count = n())

#Select only UO Mean
UO <- Progress_Mean[Progress_Mean$site == "UO",]
#Select only UPMC Mean
UPMC <- Progress_Mean[Progress_Mean$site == "UPMC",]

#Calculate mean from both sites
Both_Site_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise(BothSiteMean = mean(oc_beardragon_total, na.rm = T), n = sum(count = n()))

#Calculate mean from bear data points
Bear_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(BearMean = mean(oc_bear_total, na.rm = T), count = n())

#Calculate mean from dragon data points
Dragon_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(DragonMean = mean(oc_dragon_total, na.rm = T), count = n())

#Merge UO and UPMC site dataframes with Bear and Dragon means
UO <- merge(UO, Bear_Mean)
UO <- merge(UO, Dragon_Mean)
UPMC <- merge(UPMC, Bear_Mean)
UPMC <- merge(UPMC, Dragon_Mean)

#Change mean columns names according to site
colnames(UO)[colnames(UO) == "GroupMean"] = "UO_BearDragon"
colnames(UPMC)[colnames(UPMC) == "GroupMean"] = "UPMC_BearDragon"
colnames(UO)[colnames(UO) == "BearMean"] = "UO_Bear"
colnames(UPMC)[colnames(UPMC) == "BearMean"] = "UPMC_Bear"
colnames(UO)[colnames(UO) == "DragonMean"] = "UO_Dragon"
colnames(UPMC)[colnames(UPMC) == "DragonMean"] = "UPMC_Dragon"
colnames(UO)[colnames(UO) == "count"] = "UO_BearDragon_Original_N"
colnames(UPMC)[colnames(UPMC) == "count"] = "UPMC_BearDragon_Original_N"
colnames(Both_Site_Mean)[colnames(Both_Site_Mean) == "n"] = "BothSite_Original_N"

#Combine UO, UPMC, Both_Site, Bear and Dragon data 
Mean_Table <- data.frame(UO[,c("UO_BearDragon","GroupAssignment", "UO_Bear", "UO_Dragon")],UPMC[,c("UPMC_BearDragon", "UPMC_Bear", "UPMC_Dragon")],Both_Site_Mean[,c("BothSiteMean","BothSite_Original_N")])

#Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

#Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

#Re-order Mean Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

#Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

#Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

#Create Table
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("Bear Dragon Table Means" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = F) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")

```

##100% Table
Descriptive means table for ID's with 100% of their data.
```{r 100% Table}
#Select necessary columns for means table
Progress <- select((BearDragon_100), c(Fam_ID, GroupAssignment, timepoint, starts_with("oc")))
Progress$Row_Mean <- rowMeans(select(BearDragon_100, starts_with("oc_bd_")), na.rm = T)

#Change FamID as character and assign to ID variable
ID <- c(as.character(Progress$Fam_ID))

#Add Site column to Progress, if ID start with 9 then site is UO, else is UPMC
Progress$site <- ifelse(startsWith(ID, "9"), "UO", "UPMC")

#Group by GroupAssignment and Timepoint, and calculate Group Mean
Progress_Mean <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(GroupMean = mean(oc_beardragon_total, na.rm = T), count = n())

#Select only UO Mean
UO100 <- Progress_Mean[Progress_Mean$site == "UO",]
#Select only UPMC Mean
UPMC100 <- Progress_Mean[Progress_Mean$site == "UPMC",]

#Calculate mean from both sites
Both_Site_Mean100 <- Progress %>%
  group_by(GroupAssignment, timepoint) %>%
  summarise(BothSiteMean = mean(oc_beardragon_total, na.rm = T), n = sum(count = n()))

#Calculate mean from bear data points
Bear_Mean100 <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(BearMean = mean(oc_bear_total, na.rm = T), count = n())

#Calculate mean from dragon data points
Dragon_Mean100 <- Progress %>%
  group_by(GroupAssignment, timepoint, site) %>%
  summarise(DragonMean = mean(oc_dragon_total, na.rm = T), count = n())

#Merge UO and UPMC site dataframes with Bear and Dragon means
UO100 <- merge(UO100, Bear_Mean100)
UO100 <- merge(UO100, Dragon_Mean100)
UPMC100 <- merge(UPMC100, Bear_Mean100)
UPMC100 <- merge(UPMC100, Dragon_Mean100)

#Change mean columns names according to site
colnames(UO100)[colnames(UO100) == "GroupMean"] = "UO_BearDragon"
colnames(UPMC100)[colnames(UPMC100) == "GroupMean"] = "UPMC_BearDragon"
colnames(UO100)[colnames(UO100) == "BearMean"] = "UO_Bear"
colnames(UPMC100)[colnames(UPMC100) == "BearMean"] = "UPMC_Bear"
colnames(UO100)[colnames(UO100) == "DragonMean"] = "UO_Dragon"
colnames(UPMC100)[colnames(UPMC100) == "DragonMean"] = "UPMC_Dragon"
colnames(UO100)[colnames(UO100) == "count"] = "UO_BearDragon_100_N"
colnames(UPMC100)[colnames(UPMC100) == "count"] = "UPMC_BearDragon_100_N"
colnames(Both_Site_Mean100)[colnames(Both_Site_Mean100) == "n"] = "BothSite_100_N"

#Combine UO, UPMC, Both_Site, Bear and Dragon data 
Mean_Table <- data.frame(UO[,c("UO_BearDragon","GroupAssignment", "UO_Bear", "UO_Dragon")],UPMC[,c("UPMC_BearDragon", "UPMC_Bear", "UPMC_Dragon")],Both_Site_Mean100[,c("BothSiteMean","BothSite_100_N")])

#Convert Mean_Table, make original column as row
Mean_Table <- t(Mean_Table)

#Make Mean_Table a data frame
Mean_Table <- data.frame(Mean_Table)

#Re-order Mean Table
Mean_Table <- Mean_Table[c(5,6,7,8,9,10,11,12,1,2,3,4)]

#Add Timepoint column
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4")

#Rename column name
setnames(Mean_Table, names(Mean_Table), Timepoint_names)

#Create Table
kable(Mean_Table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  add_header_above(c(" " = 1, "Controls means" = 4, "FSU means" = 4, "DBT means" = 4)) %>%
  add_header_above(c("Bear Dragon Table Means" = 13)) %>%
  column_spec(c(1,5,9), border_right = T, include_thead = F) %>%
  column_spec(c(2,3,4,5,6,7,8,9,10,11,12,13), width_min = "2cm", width_max = "2cm")
```

##N Table
Create table for participant numbers.
```{r N Table}
#Create N table, GroupAssignment and Timepoint are dupliced here, just checking it's align
N <- data.frame(UO[, c("timepoint", "UO_BearDragon_Original_N", "GroupAssignment")],
                UO100[, c("timepoint", "UO_BearDragon_100_N", "GroupAssignment")],
                UPMC[, c("timepoint", "UPMC_BearDragon_Original_N", "GroupAssignment")],
                UPMC100[, c("timepoint", "UPMC_BearDragon_100_N", "GroupAssignment")],
                Both_Site_Mean[,c("timepoint", "BothSite_Original_N", "GroupAssignment")],
                Both_Site_Mean100[,c("timepoint", "BothSite_100_N", "GroupAssignment")]
                )

#Remove dupliced column 
N <- N[,-c(1,3,4,6,7,9,10,12,13,15,16,18,19,21,22,24,25,27)]

#Convert data frame to numeric
N <- as.data.frame(sapply(N, as.numeric))

#Transfer N table from Horzontal to Vertical
N <- data.frame(t(N))

#Calculate Total N 
N$T1 <- rowSums(N[,c(1,5,9)])
N$T2 <- rowSums(N[,c(2,6,10)])
N$T3 <- rowSums(N[,c(3,7,11)])
N$T4 <- rowSums(N[,c(4,8,12)])

#Timepoint names 
Timepoint_names <- c("T1","T2", "T3", "T4","T1","T2", "T3", "T4","T1","T2", "T3", "T4", "T1","T2", "T3", "T4")

#Rename column name 
setnames(N, names(N), Timepoint_names)

#Create Table
kable(N) %>%
  kable_styling(bootstrap_options = c("striped"), fixed_thead = T) %>%
  add_header_above(c(" " = 1, "DBT Group" = 4, "Control Group" = 4, "FSU Group" = 4, "Totals" = 4)) %>%
  add_header_above(c("Participant Numbers" = 17)) %>%
  column_spec(c(1,5,9,13), border_right = T, include_thead = F) %>%
  column_spec(2:17, width_min = "2cm", width_max = "2cm") %>%
  row_spec(7:9, background = "#d3d3d3")
```










